### 2019-08-15 document.tex
First Commit

%% ****** Start of file rsitemplate.tex ****** %
%%
%%   This file has been edited from the original source file.
%%	 The original file is part of the revtex4-1 package indicated below.
%%   Version 4.1 of 9 October 2009.
%%
%
% This is a template for producing documents for use with 
% the REVTEX 4.1 document class and the RSI substyle.
% 
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.

\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for checking your page length
%\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{siunitx}

\begin{document}

% Use the \preprint command to place your local institutional report number 
% on the title page in preprint mode.
% Multiple \preprint commands are allowed.
%\preprint{}

\title{A high-repetition-rate, fast temperature programmed gas chromatograph and
its application in comprehensive \texorpdfstring{(supercritical fluid × gas)}{supercritical fluid x gas}
chromatography } %Title of paper

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current author.
% Explanatory text should go in the []'s, 
% actual e-mail address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro for the type of information

% \affiliation command applies to all authors since the last \affiliation command. 
% The \affiliation command should follow the other information.

\author{D Malan}
\email[]{niel.malan@tuks.co.za}
\homepage[]{www.scidat.co.za}
%\thanks{}
%\altaffiliation{}
\affiliation{Department of Chemistry, University of Pretoria, Pretoria, 0002, South Africa }

\author{SJ van der Walt}
\email[]{sjvdwalt@lantic.co.za}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Department of Chemistry, University of Pretoria, Pretoria, 0002, South Africa }

\author{ER Rohwer}
\email[]{egmont.rohwer@up.ac.za}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Department of Chemistry, University of Pretoria, Pretoria, 0002, South Africa }

% Collaboration name, if desired (requires use of superscriptaddress option in \documentclass). 
% \noaffiliation is required (may also be used with the \author command).
%\collaboration{}
%\noaffiliation

\date{\today}

\keywords{high speed temperature programmed GC, subambient GC, fast process GC}
\begin{abstract}

We present a fast gas chromatographic system that can be used as a second
dimension in comprehensive (supercritical fluid × gas) chromatography
(SFC×GC). The temperature of the short (1 metre long) capillary column is
controlled by a resistively heated coaxial stainless steel tube. The electrical
resistance and therefore temperature of the stainless steel tube is measured by
continuous monitoring of the current/voltage ratio. Highly repeatable heating
rates of up to 2100 C\textdegree/min (35 C\textdegree/s) are obtained, which
should be sufficient for the most demanding fast chromatograms. To reduce the
cooling time between temperature programs the column is cooled by injecting
evaporating carbon dioxide into the space between the coaxial heater and the
column. This gives cooling rates of 5100 C\textdegree/min (85 C\textdegree/s)
which allows quick succession of temperature programs. More repeatable heating
profiles with stable GC retention times together with faster cooling are
significant improvements on previous SFC×GC systems. Cycle times of four
gas chromatograms per minute could readily be achieved, which allows efficient
coupling to high-resolution stop-flow SFC in the first dimension.

We demonstrate the fast chromatograph by separating fatty acid methyl esters by
SFC×GC chromatography, yielding fatty acid profile information which
would be useful in the food and biodiesel industries.

\end{abstract}

\pacs{}% insert suggested PACS numbers in braces on next line
{82.80.Bg}

\maketitle %\maketitle must follow title, authors, abstract and \pacs

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite and \label commands

\section{Introduction}
\label{Introduction}
% Niel: Literature review
Speed of analysis is a most important criterion for any analytical system.
Chromatography as an analytical technique is notoriously slow, compared to, say,
some spectroscopic techniques.

While it is of interest to (especially high-throughput) laboratories to reduce
run times, at some point the faster chromatography starts outstripping the
sample preparation capacity. Once the chromatographic run duration approaches
the time it takes to prepare the sample, faster chromatography will not improve
the sample throughput. Technology development in fast chromatography is
therefore driven not by conventional injection-based chromatography, but by
applications where no sample preparation is necessary and rapid results are
needed.

Examples of these would be headspace analysis for detecting
explosives\cite{Watson1991}, drugs\cite{He2014} and fuel
adulteration\cite{Hupp2018}, monitoring anaesthetic  agents in the breath of
sedated patients\cite*{Chen2014,Dong2017}, and in `electronic noses' that can
distinguish between frozen and chill-stored meat\cite{Gorska-Horczyczak2017}.
Another application for fast gas chromatography is industrial process
monitoring\cite{White2015}.

However, in the past two decades the major application for fast gas
chromatography has not been in direct sample analysis, but in the analysis of
fractions of eluate from chromatographic separations. This concept is called
\textit{comprehensively coupled chromatography}. For example, in comprehensively
coupled gas chromatography (GC×GC), fractions of a conventional gas
chromatographic run are collected by a \textit{modulator} and then admitted to a
second, fast gas chromatograph\cite{Liu1991}. GC×GC has become well
established: the annual GC×GC Symposium is in its 15th year, and major
reviews are published regularly\cite*{Seeley2013,Prebihalo2018}.

In comprehensive 2D chromatography the second dimension chromatography must be
\textit{fast}. The theory and practice of improving the speed of GC is well
developed\cite*{Cramers1999,Korytar2002}. Typically, short columns and high
carrier flows rates are used, which reduce retention times by reducing the
void time. The use of narrow-bore columns and thin films reduce run times by
improving mass transfer between the mobile and stationary phases, allowing
higher linear flow rates of the carrier gas.

Comprehensively coupled chromatography depends on \textit{orthogonality}: the
second dimension ($^2$D) separation must have a different mechanism than that of
the first dimension ($^1$D) separation\cite*{Giddings1995,Camenzuli2014}. The
higher the orthogonality, the better the \textit{separation space} offered by
the system. The different separation mechanisms that determine orthogonality are
usually provided by the different stationary phases offered by column
manufacturers, but it is also possible to use a different form of chromatography
as a first dimension: liquid chromatography has been used as a first dimension
in LC×GC\cite{Koning2004}, and in our laboratory we are developing
SFC×GC instrumentation\cite{Venter2004}.

If a chromatographic $^2$D separation is highly orthogonal to the $^1$D
separation, then we will run into the \textit{general elution
problem}\cite{Skoog2007}: it becomes unlikely that one set of acceptable
operating conditions (temperature, flow and stationary phase) will give
acceptable (fast enough and with adequate resolution) separation.

In GC×GC as it is practised today, this has become a real problem.
\textit{Wraparound} is a well-known phenomenon in
GC×GC\cite{Dalluege2003}. Wraparound happens when a peak or peaks elute
`late' on the second dimension, so late that the next modulation period has
already started before its elution and the peak appears on the next $^2$D
chromatogram.

% There are ways to avoid or ignore wraparound, but using gradient elution in
% the second dimension would, in principle, prevent all wraparound.

If wraparound is a problem in GC×GC, it becomes inevitable in
SFC×GC. The first dimension (SFC) does not normally separate compounds in
a way that correlates with vapour pressure. Indeed, SFC is particularly good in
performing group-type separations\cite{Venter1999}, where compounds with a wide
range of boiling points elute together.

\subsection{Column heating for gas chromatography}

In GC the usual solution to the general elution problem is temperature
programming, \textit{i.e.} increasing the temperature of the column throughout
the duration of the chromatograpic run. Temperature programming decreases the
retention times of late-eluting analytes without sacrificing the resolution of
early-eluting analytes. Instrument manufacturers have mastered the art of
temperature programming, and today the vast majority of 1D gas chromatography
uses temperature programming.

However, implementing temperature programming in the fast $^2$D GC poses some
challenges. Since the recommended heating rate for temperature programmed
chromatography is around \SI{10}{\celsius} per void time\cite{Blumberg2000}, the
short void times of fast chromatography imply that high heating rates are
required. Conventional air-bath GC ovens cannot attain these high heating rates,
and therefore specialized column heating is required. Resistive heating by
electric current offers a simple method, as reviewed\cite*{Wang2012,Jacobs2013},
and a recent paper\cite{Chow2017} describes the elimination of wraparound in
GC×GC of diesel samples using resistive heating to implement a simple
temperature program in the $^2$D column.

%[A system using this principle was commercially available (EZ Flash), but it's not clear if they're still on the market.]

%[The modulation period is dictated by the $^1$D peak width: to get three fractions per peak modulation periods of 1/3 of peak width at base are required.]

Of the three broad classes of resistive heating of capillary columns
identified\cite{Wang2012} (\textit{i.e.} (1) direct heating of a metal column or
conductive coating on the column, (2) coaxial heating by a conductive tube
around the column, (3) collinear heating by a heating element parallel to the
column), we have experience with direct heating and coaxial heating.

In previous work in our laboratories\cite*{Venter2004, Venter2006} a resistively
heated metal column was used. The temperature of the column was controlled by
following the temperature of a thermocouple glued to the column, but this method
had some shortcomings, like uncertainty about the absolute temperature along the
length of the column and stationary phase limitations: metal columns are often
developed for high-temperature applications, and are not available with
all the stationary phases offered in fused silica columns.

%[[The column manufacturer Restek\texttrademark{}  has 91 fused silica columns in its catalog, and only 19 metal columns.[**Restek] ]

In this work we used a coaxial heater, in the form of a thin-walled stainless
steel tube that surrounds the capillary column.  This tube is resistively heated
by controlled direct current. Due to the low thermal mass the heating is rapid,
and since the resistance of the tube indicates its temperature there is no need
for external temperature measuring devices. The benefit of this design is that
it allows the use of commercially-available fused silica columns with their wide
range of internal diameters and selectivities. Columns can be exchanged without
altering the temperature feedback system and therefore the rapid heating
characteristics. Additionally, the co-axial space between the capillary column
and the stainless steel tube can be filled with coolant to rapidly cool the
column.

\subsection{Cooling of the GC column}

At the end of temperature-programmed chromatographic run, GC columns are usually
cooled to the starting temperature by ambient air. This cooling is slow and
inefficient because of the poor conductivity and low heat capacity of air. Fast
chromatography usually implies analysis at high repetition rates, so cool-down
times also need to be shortened.

%[Hinshaw mentions the need for equilbration time after cool down in conventional
%ovens and it's impact on sample throughput.]

There have been attempts to improve the cooling rate of air baths.

Agilent\texttrademark{} markets a `low thermal mass' column, which includes
collinear heating wire and a collinear sensing element bundled with a short
silica column. These units cool down faster than normal air-baths, but only to
ambient temperature. For short columns a cooling time of \SI{1.3}{\minute} has
been reported\cite{Luong2006}. These columns are available with only a limited
range of stationary phases.

The Zip Scientific\texttrademark{} solution is forced convection. Their
`GC-Chaser' system\cite{ZipScientific} uses a blast of (chilled) room air to the
GC oven to cool it down after each GC run, allowing the use of conventional
fused silica columns. In an example\cite{ZipScientific2008} it reduces cooling
time from 16 minutes to 7 minutes. Although this can significantly decrease the
cost per analysis in a high-throughput laboratory, the cooling is not fast
enough for 2D chromatography.

The EZ Flash\texttrademark{} system uses a coaxial resistive heating system,
which allows the column to cool down ballistically. Reports from the literature
claims cool-down periods of 30 seconds\cite{Dalluege1999}.

The Valco FTP-200 fast temperature programmer\cite{VICIAGI2019} (Valco
Instruments Co. Inc.) uses a small, optional fan to cool down the columns.

Cryogenic coolers for GC ovens are available, but are intended to cool the oven
to low temperatures for the analysis of volatile compounds and not necessarily
to improve cycle times. In previous SFC×GC work in our
laboratories\cite{Venter2004, Venter2006} the cryogenic function of a Varian
3300 gas chromatograph was used to cool down the column oven at the beginning of
each run, using large quantities of coolant in the process. The resistively
heated column cooling required 30 seconds to get back to the starting
temperature in this cool environment. We estimate that a single SFC×GC
run consumed an unacceptable 15 kg of carbon dioxide coolant.

%[Venting these large amount of carbon dioxide into the workplace can possibly create a health hazard. While not toxic at low concentration, the long-term workplace exposure limit to carbon dioxide is only 5000 ppm (UK regulations\cite{HSE40}). Liquid nitrogen for cryogenic cooling is not toxic, but is expensive and requires a considerable investment in infrastructure.]

Recognizing that the precise application of coolant will require less coolant
and permit faster cooling, we developed a system that injects liquid carbon
dioxide into the space between the column and the coaxial heater. The
evaporating carbon dioxide rapidly absorbs heat from the column and coaxial
heater, achieving a high cooling rate to sub-ambient temperatures at a minimal
expense of coolant.

At the same time, the cold GC column acts as a focusing trap for the subsequent
sample, and thus forms an integral part of the modulator of the SFC×GC
system.

\subsection{Application}

The fast GC system described in this paper can be used in any application where
fast chromatograms are needed in rapid succession, for example in process
control. In our case we applied it as a $^2$D column comprehensively coupled to
a supercritical fluid chromatograph.

We applied our fast GC system to the evaluation of fatty acid profiles of
potential biodiesel feedstock. The fast GC separation was highly orthogonal to
the $^1$D separation on SFC, showcasing this type of comprehensively coupled
chromatography. An easily interpretable 2D separation was obtained, with run
times similar to the total run times required by official methods for the
determination of fatty acid profiles.

\section{Experimental}

\subsection{Introduction}

For better understanding of subsequent detail, a description of the cycle of the
SFC×GC is appropriate.

The SFC subsystem runs in stop-flow mode. The eluate of the SFC passes through a
stop valve and a static capillary restrictor. The end of the restrictor is 
inserted through the septum into the hot inlet of the GC.

After the sample is injected, the SFC runs for an optional uninterrupted period,
usually briefer than the void time. No data is collected during this time. Then
the stop valve closes and the cooling system activates to cool the GC column.
Once the column is at the set temperature, the stop valve opens and the SFC
eluate exits the restrictor into the hot splitless inlet of the GC, where it
evaporates and is transported on to the column. The vapor-phase material
is trapped in the cold stationary phase. Once the desired amount
of the SFC eluate has been collected, the stop valve closes. Some time is
allowed to pass so that the last of the evaporated SFC eluate flushes into the
column. Then the split vent of the GC inlet opens for a short period, which
vents excess carbon dioxide to the atmosphere. This normalizes the pressure in
the inlet (having been raised  by the high flow rate of CO$_2$ from the SFC) and
allows the carbon dioxide to be replaced by the pressure-controlled hydrogen
carrier gas. Once the split vent closes the GC run starts, which of course means
the start of the temperature program, which desorbs the analyte trapped on the
head of the cold column. At the end of the GC run, the cooling process starts,
cooling the column in a second or two. The next cycle then starts, marked by the
opening of SFC the stop valve.

\subsection{Hardware}
The short-cycle fast gas chromatograph was built into a modified
Varian\texttrademark{} 3300 gas chromatograph.

The inlet was an unmodified Varian\texttrademark{} 1075 split/splitless inlet.
The temperature control of the inlet was by the original electronics, controlled
from the Varian 3300 front panel. The split vent valve was disconnected from the
gas chromatograph, and controlled from the control computer described below.

The detector was an unmodified Varian\texttrademark{} 3300 flame ionization
detector (FID). The temperature of the detector was controlled by the original
electronics, controlled from the front panel. The detector bias voltage was
supplied by the original electronics, but a stand-alone high-speed electrometer
(V.G. Micromass Ltd, Model M406-H) captured the signal, which was then
conditioned by a bench-top amplifier (V.G. Micromass Ltd, Model M406) before it
was sent to the computer.

The coaxial heater was made of a 940 mm length of 304 stainless steel, obtained
from MIFAM (Milanówek, Poland). It had an outside diameter of 1.06 mm and an
inside diameter of 0.80 mm.

The ends of the coaxial heater tube terminated in two identical, specially
designed T-piece blocks. These blocks fulfilled three roles: It (1) sealed the
coaxial tube to contain coolant, (2) allowed electrical connection to the
coaxial heater, and (3) acted as a heated transfer line between the column and
the detector and inlet.

The T-piece blocks were machined from brass. The stainless steel tube of the
coaxial heater was brazed onto the block. The cooling CO$_2$ was let in from one
side, and on the opposite side a thermocouple probe inserted into a blind hole
measured the temperature of the block. A micro-union using a metal ferrule
(Restek\texttrademark{} SilTite $\mu$-Union Connectors), brazed to the block,
was used to seal the capillary column. An electrical contact was added, to which
an electrical conductor could be soft-soldered. Four holes through the length of
the block allowed the fitting of four 220V, 100 W heater cartridges (Hotset),
providing each of the two blocks 400W of heating.

\begin{figure}
	\includegraphics[width=8.5cm]{./Figures/Cutaway_with_symbols.png}
	\caption["The T-piece block"]{A cutaway diagram of the inlet/outlet outlet T-piece blocks, showing the (a) cryogenic coolant inlet/outlet, (b) the coaxial heater, (c) the capillary column, (d) the mico-union seal, (e) the cartridge heater socket, (f) the thermocouple socket, and (g) the electrical connection.}%
	\label{fig:Manifold}
\end{figure}

The chromatographic column entered the T-piece block via the bottom port with the
coaxial heater tube, and passed out through the top port and into the inlet or
detector.

%A blind hole on the right-hand side of the manifold mounted a thermocouple. The
%temperature reported by the thermocouple was fed to control software, which
%controlled the temperature of the manifold.

In the left-hand side of the T-piece block was the inlet or outlet port for the
carbon dioxide coolant.

Since the coaxial heater resistance measurement used a two-wire technique, the
current-carrying circuit was made entirely of soldered joints to minimize stray
resistance from developing in electrical connections.

The T-piece blocks were mounted on `cars' that slid up and down twin round-bar
rails on brass bushes. The cars carried the weight of the inlet and outlet
T-piece blocks and rigidly aligned the column with the inlet and detector of the
gas chromatograph. The cars were isolated electrically from the rails by a
sandwich construction that included silicone-impregnated mica as insulating material. The
whole of the inlet and outlet T-piece blocks were at the electrical potential of
the coaxial heater ends.

The cryogenic carbon dioxide (Afrox, Tec (Wet)) was supplied from a cylinder
equipped with a dip tube. It flowed to a coil heat exchanger bathed in a cold
(-5 \textdegree C) propylene glycol heat transfer fluid, which was mounted on
top of the Varian GC. From the heat exchanger the carbon dioxide flowed down to
the cryo shut-off valve (ASCO, RedHat brand). This arrangement ensured a supply
of liquid CO$_2$ at the shut-off valve, without which some gaseous CO$_2$ might
have to vent through the coaxial heater before the liquid CO$_2$ coolant could
reach it. Downstream of the shut-of valve there was a 10-turn metering valve,
which controlled the flow of carbon dioxide into the coaxial heater for
evaporative cooling. At the outlet end of the coaxial heater the carbon dioxide
escaped through the T-piece block into the atmosphere.

The SFC subsystem consisted of five packed silica columns (150 mm × 4.6
mm, 3 $\mu$m particles) (Restek, Pinnacle DB Silica) in series, a sample valve
(VICI), and a stop valve (VICI). Carbon dioxide, (99.995 \% purity, Air
Products) was supplied to a Varian 8500 piston pump. The inlet pressure of the
SFC columns was controlled by a software proportional controller driving the
stepper motor of the piston pump. The high pressure at the column exit was
maintained by a fused silica capillary restrictor with an internal diameter of
\SI{0.050}{\milli\metre}, \SI{800}{\milli\metre} long.

\subsection{Electronics}

The electronics for controlling the fast temperature programmed gas
chromatograph and the SFC front-end was developed in-house.

A controlled direct current was used to heat the coaxial heater. The heating
circuit consisted of the coaxial heater in series with a reference resistor and
a ballast resistor. The reference resistor was constructed out of parallel
stainless steel wires with an open construction to promote heat dissipation with
the aim of keeping its temperature constant. The ballast resistor was of stainless
steel wire in a bifilar winding with an air core, to minimize electromagnetic
interference and encourage heat dissipation.

The resistance of the reference resistor ($R_{ref}$) was about \SI{0.005}{\ohm},
and the resistance of the coaxial heater ($R_{col}$) was about  \SI{0.3}{\ohm}, so
that most of the heat in the circuit was dissipated by the coaxial heater.
The potential difference across the coaxial heater ($V_{col}$) and the reference
resistor ($V_{ref}$) were measured (See Figure \ref{Circuit}). If the
resistances of the coaxial heater and the reference resistor were both constant,
the ratio $V_{col}/V_{ref}$ would be constant, independent of the current.
But metals have positive coefficients of resistivity so the resistance of the
coaxial heater will increase with temperature. If the assumption is made that
the temperature of the reference resistor does not change, then the ratio
$V_{col}/V_{ref}$ will be proportional to $R_{col}$. If the resistance $R_{col}$ is
assumed to be a monotonically rising function of the temperature ($R_{col} = f(T)$),
then the inverse function will provide the temperature ($T = f^{-1}(R_{col})$).

\begin{figure}
\includegraphics[width=8.5cm]{./Figures/ResistanceMeasurement.pdf}%
\caption{\label{Circuit}A simplified circuit diagram of the resistance measuring circuit.}%
\end{figure}

A bank of six PNP 2N2955 bipolar transistors mounted in parallel on an aluminium
plate provided a controlled current of up to \SI{20}{\ampere} at \SI{20}{\volt}
for the coaxial heater. Their mounting plate was air-cooled by two 4-inch fans.

A two-stage control system controlled the current. The first stage of the
control system was a PID controller implemented in LabVIEW. The process variable
was the temperature of the coaxial heater, as calculated from its electrical
resistance, and the set value was determined by the desired chromatographic
temperature program. The manipulated variable was the voltage of the
digital-to-analog converter converter (DAC) of the data acquisition board. The
final stage was an electronic system, where the voltage applied to the coaxial
heater was the process variable, and the set value was a voltage provided by the
DAC. The manipulated variable was the base current of the power transistors.
In summary, the software set a voltage, which set the power of the coaxial
heater. The two-stage design allows for switching of the power to the coaxial
heater from computer control to manual control by a potentiometer on the
instrument front panel. Being able to control the power of the coaxial heater
manually is extremely useful during development and fault-finding.

AD595 monolithic thermocouple amplifiers (Analog Devices) with integral cold
junction compensation was used to condition the signal of the K-type
thermocouples that were used for temperature monitoring and calibration.

Solid state relays (Opto 22, Model 240D3) were used to switch the inlet and
outlet T-piece block cartridge heaters (described above) on and off. Pulse width
modulation, implemented in software, was used to control the amount of heat
produced by the cartridge heaters, and hence the temperature of the T-piece blocks.

A PCI-6014 multifunction data acquisition board (National
Instruments\texttrademark{}) was used to interface the electronics with the
computer.

\subsection{Coaxial heater temperature calibration}

The temperature of the coaxial heater was calibrated by constructing a
thermocouple probe from 0.025 mm diameter thermocouple alloy wire (T1 and T2
alloys, Goodfellow) threaded inside a 500 mm length of 0.25 mm i.d.
capillary chromatography column. This thermocouple was then threaded inside the
coaxial heater (just like the capillary column during GC operation), to record
the temperature of the heater. The recorded temperature could then be used to
calibrate the coaxial heater resistance.

\subsection{Heating uniformity}

To determine whether the coaxial heater was heating the column with acceptable
uniformity, we used two methods. First, we acquired thermal images of the
coaxial heater, using a FLIR T660 infrared camera. Secondly, for experiments in
determining temperature gradients, a thermocouple probe was constructed as
described above, except that the probe contained two thermocouples, 330 mm
apart, equidistant from the ends.

\subsection{Software}

\subsubsection{Instrument Control}
The software for controlling the instrument and collecting data was written in
LabVIEW 7.1\texttrademark{} (National Instruments).
% The multi-threading capabilities of LabVIEW greatly eased development. Each
% subsystem of the instrument was controlled by a separate loop, allowing it to
% run at its own rate. In particular, running the manifold heater controls and
% pressure control as separate threads from the chromatography control and data
% loops simplified development.
Two main loops were used. One controlled the various aspects of the instrument,
in particular the temperature control. This loop ran with a  period of 200 ms.
The second main loop collected the data and ran as often as the hardware
allowed.

The coaxial heater temperature was controlled by
proportional-integral-derivative (PID) controllers implemented in LabVIEW. In
practice it was found that only proportional and integrative control was needed.
We used a privately published\cite{Peacock2008} step-by-step implementation of
the Cohen-Coon loop tuning method.

Subsidiary PID controllers controlled the T-piece block temperatures and the
CO$_2$ pump pressure.

%The version of LabVIEW used did not have any real-time capability, so timings are approximate and indeterminate, but good enough for chromatography.

\subsubsection{Data structure}
In GC×GC, 2D data is recorded as a continuous FID output stream, as if it
is a 1D GC chromatogram, and later converted into a 2D chromatogram, using
knowledge of the modulation period.

For two reasons we could not use this approach. Firstly, in our instrument the
first (SFC) dimension runs in a stop-flow mode making continuous data recording
inappropriate. Secondly, the duration of the cooling cycle can vary slightly,
which could introduce unacceptable variation in \textsuperscript{2}D retention
times.

We therefore constructed 2D chromatograms by starting to record data each time
the GC fast temperature program started, noting the GC start time as the elution
time of the first (SFC) dimension.

\subsubsection{Data visualization}
For data visualization we used the technical computing system Mathematica
11.3\texttrademark{} (Wolfram).  First the collected data was converted to a
list of three-element lists, with $^1$D retention time, $^2$D retention time,
and detector signal as the elements of the inner lists. The Mathematica
functions \texttt{List3DPlot[]} and \texttt{ContourPlot[]} could then be used to
plot 3D chromatograms or contour plots respectively.

\section{Results and Discussion}

\subsection{Heating uniformity}

As a first step in developing the coaxial heater, we tried to answer the
question about its temperature uniformity. Because the temperature coefficient
of resistivity of metals is positive, in the absence of equalizing heat flow the
resistive heating process in a long, thin tube is inherently unstable. To
monitor the temperature profile along the length, we acquired a thermal video
(Figure \ref{fig:ThermImg}) of the coaxial heater. The video shows that the
coaxial heater heats and cools smoothly with no run-away hot spots.

%Modeling the coaxial heater thermo-electrically might be a fruitful exercise.

\begin{figure}
\includegraphics[width=8.5cm]{./Figures/1-16.jpg}%
\caption{\label{fig:ThermImg}A thermal image of the coaxial heater.}%
\end{figure}

To quantify the non-uniformity of the coaxial heater, a dual thermocouple probe
was inserted into the coaxial heater. The two thermocouples in the probe were
330 mm apart and positioned in the central third of the coaxial heater. The
coaxial heater was submitted to a repeated program of cooling and ballistic
heating. Figure \ref{fig:Repeatability} shows that the gradients established by
cooling was small (approximately \SI{10}{\celsius}), stable and repeatable, and
should not prevent good chromatography.

\begin{figure}
	\includegraphics[width=8.5cm]{./Figures/cp.pdf}%
	\caption{\label{fig:Repeatability}A graph indicating that temperature gradients are modest, stable and repeatable}%
\end{figure}

\subsection{Temperature calibration}

While it is conceptually possible to have a fast temperature program by using
the voltage/current ratio alone as a temperature indicator and controlled
variable, it would be hard to design chromatographic methods or translate
methods without a knowledge of the real temperature. Therefore we went to some
effort to calibrate the coaxial heater.

To calibrate a thermometer, the thermometer under test and its calibration
environment must be in equilibrium. This requirement is hard to meet in our
calibration, because a single point (the junction of the thermocouple) needs to
be in equilibrium with the length of the coaxial heater at all times during fast
heating. This equilibrium would be very difficult to maintain, especially
because the uniformity of heating cannot be guaranteed, and is additionally
influenced by the presence of the T-piece heaters at the high temperature of the
GC inlet and detector --- for a totally uniform heating of the coaxial heater the
T-piece blocks would have to be at the same temperature as the coaxial heater.

% In a more pragmatic approach we did some experiments to determine how much of a
%temperature difference can be generated in the coaxial heater. A
%dual-thermocouple probe was constructed, and used to measure temperatures 330 mm
%apart in the coaxial heater. Using this we could determine that the temperature
%gradients along the length of the coaxial heater generated by heating and
%cooling was modest, stable and repeatable.

%This convinced us that a resistance measurement calibrated against temperature
%would furnish a meaningful measure of real temperature, as long as one kept the
%non-linearity in mind.

For reasons not understood, the calibration curve is oddly curved, and we
arbitrarily fitted a B-spline to the data points. This procedure can be
automated\cite{WenniZheng2012}. Points from this B-spline curve were then
extracted to create a calibration curve, from which an estimate of the
temperature can be calculated by linear interpolation\cite{Possolo2017}.

\begin{figure}
\includegraphics[width=8.5cm]{./Figures/2015_04_24_Calibration.pdf}%
\caption{\label{TempCal}A calibration curve.}%
\end{figure}

\subsection{Heating rate}

To achieve good resolution in temperature-programmed chromatography, a good rule
of thumb for the heating rate is \SI{10}{\celsius} per void
time\cite{Blumberg2000}. With hydrogen as carrier gas in a
\SI{0.25}{\milli\metre} i.d. column of the optimum linear velocity is
\SI{40}{\centi\metre\per\second}. Then the void time of a \SI{1}{\metre} column
is \SI{2.5}{\s}, so the recommended heating rate is \SI{10}{\celsius} per
\SI{2.5}{\s}, which is \SI{4}{\celsius}/s, or \SI{240}{\celsius\per\minute}.
Since in fast chromatography excess peak resolution is traded for shorter run
times, higher than optimum flow rates will be used, so higher heating rates will
be required. For narrower columns the flow will be even higher so heating rates
of more than 1000 C\textdegree/min will be required.

The attainable heating rate is a function of power to the heater and of the
temperature required. (In the instrument presented here power was limited by the
voltage output range of the DAC of the data acquisition board, and not by the
power of the heater.) We were able to maintain controlled heating rates of 
2500 C\textdegree /min up to 400 \textdegree C, or up to 4000 C\textdegree /min
up to 350 \textdegree C. (Figure \ref{fig:MaxHeatingRate})

The heating rates attainable seem to be sufficient for the most demanding fast
gas chromatography.

\begin{figure}
\includegraphics[width=8.5cm]{./Figures/high_rate_heating.pdf}%

\caption{\label{fig:MaxHeatingRate}A graph of 9 identical, consecutive temperature ramps overlaid. 
The heating rate is 4000 C\textdegree /min. The temperature follows the setpoint faithfully up to \SI{350}{\celsius}}

\end{figure}

\subsection{Cooling rate}

Using evaporating carbon dioxide as a powerful coolant, it was possible to cool
down the column at a rate of 5100 C$^\circ$/min. The cooling rate depends on the
setting of the metering valve, with the lowest coaxial heater temperatures and
smallest gradients achieved at an intermediate flow of about
\SI{30}{\gram\per\minute}.

%At high flows the coaxial heater fills with liquid carbon dioxide, with
%evaporation taking place only at the outlet end. At low flow, evaporation takes
%place only at the inlet end, the rest of the coaxial heater being filled with
%gaseous carbon dioxide. This was easily deduced by observing the layer of frost
%from atmospheric water forming on the coaxial heater. Under ideal conditions the
%frost would form a continuous layer on the outside of the coaxial heater, which
%also gave the lowest temperature and best cooling rate.

\subsection{Repeatability}

Comprehensively coupled chromatography depends heavily on repeatable
\textsuperscript{2}D separations. To test for chromatographic repeatability, we
added small amounts of hydrocarbons to the \textsuperscript{1}D mobile phase.
They are unretained on the silica stationary phase. Because they are not
retained, they are present in every fraction of the SFC eluate in equal amounts,
and therefore they should yield identical \textsuperscript{2}D chromatograms.

Results obtained from creating a 2D blank chromatogram with two alkanes in the
mobile phase is summarized in Table \ref{tab:table1}. Peak widths were about
\SI{500}{\milli\second}. The relative standard deviations (RSD) of retention
times were similar to those obtained in GC×GC\cite{Shellie2002}.

\begin{table}

\caption{\label{tab:table1}A summary of retention time repeatability of alkanes
separated on the fast temperature programmed chromatograph.}

\begin{ruledtabular}
\begin{tabular}{lllll}
Compound & n & t\textsubscript{r} (s) & S.D. of t\textsubscript{r} (s)& R.S.D. of t\textsubscript{r} (\%)\\
\hline
Dodecane & 73 & 5.069 & 0.0231 & 0.456\\
Hexadecane & 73 & 6.584 & 0.0516 & 0.784\\
\end{tabular}
\end{ruledtabular}
\end{table}

\subsection{Chromatography}

Comprehensively coupled chromatography is made possible by having different
retention mechanisms in the columns of the two dimensions. When fatty acid
methyl esters (FAMEs) are chromatographically separated on bare silica with pure
carbon dioxide as a mobile phase, they are separated according to the number of
double bonds, independent of chain length\cite{Smith2001}. On a GC column, FAMEs
are separated according to volatility or, equivalently, chain length. Therefore,
when SFC and GC are comprehensively coupled, we can expect FAMEs to have a
highly orthogonal separation.

We prepared FAMEs by esterifying oil samples, following an official
method\cite{AOCS2017}. Of these samples, \SI{0.2}{\micro\litre} was injected
into the pure carbon dioxide mobile phase at \SI{200}{\bar} and room temperature
and eluted through bare silica.

We collected 10-second fractions of SFC eluate on the cold GC column. The fast
temperature program ramped the GC column temperature from \SI{-20}{\celsius} to
\SI{350}{\celsius} in \SI{10}{s} (\SI{2200}{\celsius\per\second}), then
maintaining \SI{350}{\celsius} for \SI{2}{\second}. Then the cooling system
would activate and cool the column to \SI{-20}{\celsius} or below, ready to trap
the next SFC fraction.

In this way a series of GC chromatograms of SFC fractions were recorded, which
could be assembled into a 2D chromatogram. Figure \ref{fig:2DChromatogram} shows
a 2D chromatogram of a sample of FAME prepared from canola oil. This 2D
chromatogram consists of 132 fast GC chromatograms collected in approximately 90
minutes.

\begin{figure}
\includegraphics[width=8.5cm]{./Figures/Interpretation.png}%

\caption{\label{fig:2DChromatogram}A 2D chromatogram of FAMEs derived from
canola oil. It is clear that the oil consists mostly of unsaturated fatty
acids.}%

\end{figure}

\section{Conclusion}

To our knowledge, the cycle time of this new temperature programmed GC is
unmatched in the literature, and it allows for the improved performance of
SFC×GC instruments. The fast GC will be of interest to all GC analyses of
highly dynamic chemical systems, including on-line monitoring and control of
fast laboratory or industrial reactions.

The low thermal mass of the heater and column simplifies heating and cooling of
a portable fast GC, reducing electrical and carbon dioxide coolant requirements.
When sub-ambient temperatures and extreme cycle times are not essential,
compressed air could also serve to cool the column.

% If in two-column mode, this environment will change to single-column format so that long equations can be displayed. 
% Use only when necessary.
%\begin{widetext}
%$$\mbox{put long equation here}$$
%\end{widetext}

% Figures should be put into the text as floats. 
% Use the graphics or graphicx packages (distributed with LaTeX2e). EPSFig is no longer fully supported.
% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz, and Frank Mittelbach for examples. 
%
% Here is an example of the general form of a figure:
% Fill in the caption in the braces of the \caption{} command. 
% Put the label that you will use with \ref{} command in the braces of the \label{} command.
%
% \begin{figure}
% \includegraphics{}% % Important NOTE: Please make certain your figures do not include local directory paths. ex. "c:\file\sub\fig1.eps"
% \caption{\label{}}%
% \end{figure}

% Tables may be be put in the text as floats.
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
%
% \begin{table}
% \caption{\label{} }
% \begin{tabular}{}
% \end{tabular}
% \end{table}

\section*{Supplementary Material}

In the supplementary material we provide a thermographic video of the coaxial
heater heating and cooling, which indicates the evenness of heating and the
rapidity of cooling.

% If you have acknowledgments, this puts in the proper section head.

\begin{acknowledgments}
%Put your acknowledgments here.

Prof. Walter Meyer of the Department of Physics at the University of Pretoria
supplied the idea for the electronics that measure the resistance of the
stainless steel heating tube. Nico van Vuuren machined the T-piece blocks and
their mounting rails. We thank Restek for the generous donation of the packed
silica columns. Reinhardt Heymans from FLIR Systems recorded the thermal images
at no cost. David Masemula kept the laboratory supplied with consumables.

\end{acknowledgments}

% Create the reference section using BibTeX:
\bibliography{RSI-2019_05}
% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"

\end{document}
%
% ****** End of file aiptemplate.tex ******

### 2019-09-14 document.tex
Paper as submitted to RSI

@@
 
-\title{A high-repetition-rate, fast temperature programmed gas chromatograph and
-its application in comprehensive \texorpdfstring{(supercritical fluid × gas)}{supercritical fluid x gas}
-chromatography } %Title of paper
+\title{A high-repetition-rate, fast temperature-programmed gas chromatograph and
+its on-line coupling to a supercritical fluid chromatograph (SFC×GC)}
+%Title of paper
 
@@
 
-\keywords{high speed temperature programmed GC, subambient GC, fast process GC}
+\keywords{high speed temperature programmed GC, sub-ambient GC, fast process GC}
 \begin{abstract}
@@
 We present a fast gas chromatographic system that can be used as a second
-dimension in comprehensive (supercritical fluid × gas) chromatography
-(SFC×GC). The temperature of the short (1 metre long) capillary column is
-controlled by a resistively heated coaxial stainless steel tube. The electrical
-resistance and therefore temperature of the stainless steel tube is measured by
-continuous monitoring of the current/voltage ratio. Highly repeatable heating
-rates of up to 2100 C\textdegree/min (35 C\textdegree/s) are obtained, which
-should be sufficient for the most demanding fast chromatograms. To reduce the
-cooling time between temperature programs the column is cooled by injecting
+dimension in comprehensive (supercritical fluid × gas) chromatography (SFC×GC).
+The temperature of the short (1 metre long) capillary column is controlled by a
+resistively heated coaxial stainless-steel tube. The electrical resistance and
+therefore temperature of the stainless-steel tube is measured by continuous
+monitoring of the current/voltage ratio. Highly repeatable heating rates of up
+to \SI{2100}{\celsius\per\minute} (\SI{35}{\celsius\per\second}) are obtained,
+which should be high enough for the most demanding fast chromatograms. To reduce
+the cooling time between temperature programs the column is cooled by injecting
 evaporating carbon dioxide into the space between the coaxial heater and the
-column. This gives cooling rates of 5100 C\textdegree/min (85 C\textdegree/s)
-which allows quick succession of temperature programs. More repeatable heating
-profiles with stable GC retention times together with faster cooling are
-significant improvements on previous SFC×GC systems. Cycle times of four
-gas chromatograms per minute could readily be achieved, which allows efficient
-coupling to high-resolution stop-flow SFC in the first dimension.
-
-We demonstrate the fast chromatograph by separating fatty acid methyl esters by
-SFC×GC chromatography, yielding fatty acid profile information which
-would be useful in the food and biodiesel industries.
+column. This gives cooling rates of \SI{5100}{\celsius\per\minute}
+(\SI{85}{\celsius\per\minute}) which allows quick succession of temperature
+programs. More repeatable heating profiles with stable GC retention times
+together with faster cooling are significant improvements on previous SFC×GC
+systems. Cycle times of four gas chromatograms per minute could readily be
+achieved, which allows efficient coupling to high-resolution stop-flow SFC in
+the first dimension. We demonstrate the fast chromatograph by separating fatty
+information which would be useful in the food and biodiesel industries.
 
@@
 chromatographic run are collected by a \textit{modulator} and then admitted to a
-second, fast gas chromatograph\cite{Liu1991}. GC×GC has become well
-established: the annual GC×GC Symposium is in its 15th year, and major
-reviews are published regularly\cite*{Seeley2013,Prebihalo2018}.
+second, fast gas chromatograph\cite{Liu1991}. GC×GC has become well established:
+the annual GC×GC Symposium is in its 15th year, and major reviews are published
+regularly\cite*{Seeley2013,Prebihalo2018}.
 
-In comprehensive 2D chromatography the second dimension chromatography must be
+In comprehensive 2D chromatography the second-dimension chromatography must be
 \textit{fast}. The theory and practice of improving the speed of GC is well
@@
 
-In this work we used a coaxial heater, in the form of a thin-walled stainless
-steel tube that surrounds the capillary column.  This tube is resistively heated
-by controlled direct current. Due to the low thermal mass the heating is rapid,
-and since the resistance of the tube indicates its temperature there is no need
-for external temperature measuring devices. The benefit of this design is that
-it allows the use of commercially-available fused silica columns with their wide
-range of internal diameters and selectivities. Columns can be exchanged without
-altering the temperature feedback system and therefore the rapid heating
-characteristics. Additionally, the co-axial space between the capillary column
-and the stainless steel tube can be filled with coolant to rapidly cool the
-column.
+In this work we used a coaxial heater, in the form of a thin-walled
+stainless-steel tube that surrounds the capillary column.  This tube is
+resistively heated by controlled direct current. Due to the low thermal mass the
+heating is rapid, and since the resistance of the tube indicates its temperature
+there is no need for external temperature measuring devices. The benefit of this
+design is that it allows the use of commercially-available fused silica columns
+with their wide range of internal diameters and selectivities. Columns can be
+exchanged without altering the temperature feedback system and therefore the
+rapid heating characteristics. Additionally, the co-axial space between the
+capillary column and the stainless steel tube can be filled with coolant to
+rapidly cool the column.
 
@@
 
-Agilent\texttrademark{} markets a `low thermal mass' column, which includes
+Agilent\texttrademark{} markets a `low thermal mass' column, which includes a
 collinear heating wire and a collinear sensing element bundled with a short
@@
 The Zip Scientific\texttrademark{} solution is forced convection. Their
-`GC-Chaser' system\cite{ZipScientific} uses a blast of (chilled) room air to the
+`GC-Chaser' system uses a blast of (chilled) room air to the
 GC oven to cool it down after each GC run, allowing the use of conventional
@@
 
-Cryogenic coolers for GC ovens are available, but are intended to cool the oven
+Cryogenic coolers for GC ovens are available but are intended to cool the oven
 to low temperatures for the analysis of volatile compounds and not necessarily
@@
 heated column cooling required 30 seconds to get back to the starting
-temperature in this cool environment. We estimate that a single SFC×GC
-run consumed an unacceptable 15 kg of carbon dioxide coolant.
+temperature in this cool environment. We estimate that a single SFC×GC run
+consumed an unacceptable 15 kg of carbon dioxide coolant.
 
@@
 usually briefer than the void time. No data is collected during this time. Then
-the stop valve closes and the cooling system activates to cool the GC column.
+the stop valve closes, and the cooling system activates to cool the GC column.
 Once the column is at the set temperature, the stop valve opens and the SFC
@@
 from the Varian 3300 front panel. The split vent valve was disconnected from the
-gas chromatograph, and controlled from the control computer described below.
+gas chromatograph and controlled from the control computer described below.
 
@@
 
-The coaxial heater was made of a 940 mm length of 304 stainless steel, obtained
-from MIFAM (Milanówek, Poland). It had an outside diameter of 1.06 mm and an
-inside diameter of 0.80 mm.
+The coaxial heater was made of a 940 mm length of stainless steel (SAE 304
+grade), obtained from MIFAM (Milanówek, Poland). It had an outside diameter of
+1.06 mm and an inside diameter of 0.80 mm.
 
@@
 
-The T-piece blocks were machined from brass. The stainless steel tube of the
+The T-piece blocks were machined from brass. The stainless-steel tube of the
 coaxial heater was brazed onto the block. The cooling CO$_2$ was let in from one
@@
 \begin{figure}
-	\includegraphics[width=8.5cm]{./Figures/Cutaway_with_symbols.png}
+	\includegraphics[width=\textwidth]{./Figures/Cutaway_with_symbols.png}
 	\caption["The T-piece block"]{A cutaway diagram of the inlet/outlet outlet T-piece blocks, showing the (a) cryogenic coolant inlet/outlet, (b) the coaxial heater, (c) the capillary column, (d) the mico-union seal, (e) the cartridge heater socket, (f) the thermocouple socket, and (g) the electrical connection.}%
@@
 The chromatographic column entered the T-piece block via the bottom port with the
-coaxial heater tube, and passed out through the top port and into the inlet or
-detector.
+coaxial heater tube and passed out through the top port and into the inlet or
+detector. In the left-hand side of the T-piece block was the inlet or outlet port for the
+carbon dioxide coolant.
 
@@
 %controlled the temperature of the manifold.
-
-In the left-hand side of the T-piece block was the inlet or outlet port for the
-carbon dioxide coolant.
 
@@
 equipped with a dip tube. It flowed to a coil heat exchanger bathed in a cold
-(-5 \textdegree C) propylene glycol heat transfer fluid, which was mounted on
+\SI{-5}{\celsius}) propylene glycol heat transfer fluid, which was mounted on
 top of the Varian GC. From the heat exchanger the carbon dioxide flowed down to
@@
 a ballast resistor. The reference resistor was constructed out of parallel
-stainless steel wires with an open construction to promote heat dissipation with
-the aim of keeping its temperature constant. The ballast resistor was of stainless
-steel wire in a bifilar winding with an air core, to minimize electromagnetic
-interference and encourage heat dissipation.
+stainless-steel wires with an open construction to promote heat dissipation with
+the aim of keeping its temperature constant. The ballast resistor was of
+stainless-steel wire in a bifilar winding with an air core, to minimize
+electromagnetic interference and encourage heat dissipation.
 
@@
 \begin{figure}
-\includegraphics[width=8.5cm]{./Figures/ResistanceMeasurement.pdf}%
+\includegraphics[width=\textwidth]{./Figures/ResistanceMeasurement.pdf}%
 \caption{\label{Circuit}A simplified circuit diagram of the resistance measuring circuit.}%
@@
 In summary, the software set a voltage, which set the power of the coaxial
-heater. The two-stage design allows for switching of the power to the coaxial
+heater. The two-stage design allows for switching of the control of the coaxial
 heater from computer control to manual control by a potentiometer on the
@@
 \begin{figure}
-\includegraphics[width=8.5cm]{./Figures/1-16.jpg}%
+\includegraphics[width=\textwidth]{./Figures/1-16.jpg}%
 \caption{\label{fig:ThermImg}A thermal image of the coaxial heater.}%
@@
 \begin{figure}
-	\includegraphics[width=8.5cm]{./Figures/cp.pdf}%
+	\includegraphics[width=\textwidth]{./Figures/cp.pdf}%
 	\caption{\label{fig:Repeatability}A graph indicating that temperature gradients are modest, stable and repeatable}%
@@
 variable, it would be hard to design chromatographic methods or translate
-methods without a knowledge of the real temperature. Therefore we went to some
+methods without a knowledge of the real temperature. Therefore, we went to some
 effort to calibrate the coaxial heater.
@@
 calibration, because a single point (the junction of the thermocouple) needs to
-be in equilibrium with the length of the coaxial heater at all times during fast
-heating. This equilibrium would be very difficult to maintain, especially
+be in equilibrium with the length of the coaxial heater during the whole of fast
+heating cycle. This equilibrium would be very difficult to maintain, especially
 because the uniformity of heating cannot be guaranteed, and is additionally
 influenced by the presence of the T-piece heaters at the high temperature of the
-GC inlet and detector --- for a totally uniform heating of the coaxial heater the
-T-piece blocks would have to be at the same temperature as the coaxial heater.
+GC inlet and detector --- for a totally uniform heating of the coaxial heater
+the T-piece blocks would have to be at the same temperature as the coaxial
+heater. Acknowledging these limitations, we performed a calibration procedure
+assuming that the thermocouple junction was in equilibrium with the coaxial
+heater, which was assumed to be of uniform temperature over its length.
 
@@
 
-For reasons not understood, the calibration curve is oddly curved, and we
-arbitrarily fitted a B-spline to the data points. This procedure can be
-automated\cite{WenniZheng2012}. Points from this B-spline curve were then
-extracted to create a calibration curve, from which an estimate of the
+For reasons not understood, the calibration (see Figure \ref{TempCal}) curve is
+oddly curved, and we arbitrarily fitted a B-spline to the data points. This
+procedure can be automated\cite{WenniZheng2012}. Points from this B-spline curve
+were then extracted to create a calibration curve, from which an estimate of the
 temperature can be calculated by linear interpolation\cite{Possolo2017}.
@@
 \begin{figure}
-\includegraphics[width=8.5cm]{./Figures/2015_04_24_Calibration.pdf}%
-\caption{\label{TempCal}A calibration curve.}%
+\includegraphics[width=\textwidth]{./Figures/2019_07_12_B-spline_fit_CPlot.pdf}%
+
+\caption{\label{TempCal}A calibration curve of the coaxial heater. The markers
+were obtained from a B-spline fitted manually to the curve. The temperature is
+obtained by linear interpolation between markers.}%
+
 \end{figure}
@@
 be required. For narrower columns the flow will be even higher so heating rates
-of more than 1000 C\textdegree/min will be required.
+of more than \SI{1000}{\celsius\per\minute} will be required.
 
@@
 power of the heater.) We were able to maintain controlled heating rates of
-2500 C\textdegree /min up to 400 \textdegree C, or up to 4000 C\textdegree /min
-up to 350 \textdegree C. (Figure \ref{fig:MaxHeatingRate})
-
-The heating rates attainable seem to be sufficient for the most demanding fast
-gas chromatography.
+\SI{2500}{\celsius\per\minute} up to \SI{400}{\celsius}, or up to \SI{4000}{\celsius\per\minute}
+up to \SI{350}{\celsius}. (Figure \ref{fig:MaxHeatingRate}.) The heating rates
+attainable seem to be high enough for the most demanding fast gas
+chromatography.
 
 \begin{figure}
-\includegraphics[width=8.5cm]{./Figures/high_rate_heating.pdf}%
+\includegraphics[width=\textwidth]{./Figures/high_rate_heating.pdf}%
 
-\caption{\label{fig:MaxHeatingRate}A graph of 9 identical, consecutive temperature ramps overlaid. 
-The heating rate is 4000 C\textdegree /min. The temperature follows the setpoint faithfully up to \SI{350}{\celsius}}
+\caption{\label{fig:MaxHeatingRate}A graph of 9 identical, consecutive
+temperature ramps overlaid. The heating rate is \SI{4000}{\celsius\per\minute}.
+The temperature follows the setpoint faithfully up to \SI{350}{\celsius}}
 
@@
 Using evaporating carbon dioxide as a powerful coolant, it was possible to cool
-down the column at a rate of 5100 C$^\circ$/min. The cooling rate depends on the
-setting of the metering valve, with the lowest coaxial heater temperatures and
-smallest gradients achieved at an intermediate flow of about
+down the column at a rate of \SI{5100}{\celsius\per\minute}. The cooling rate
+depends on the setting of the metering valve, with the lowest coaxial heater
+temperatures and smallest gradients achieved at an intermediate flow of about
 \SI{30}{\gram\per\minute}.
@@
 Results obtained from creating a 2D blank chromatogram with two alkanes in the
-mobile phase is summarized in Table \ref{tab:table1}. Peak widths were about
-\SI{500}{\milli\second}. The relative standard deviations (RSD) of retention
-times were similar to those obtained in GC×GC\cite{Shellie2002}.
+mobile phase is summarized in Table \ref{tab:table1}. The peak widths were about
+\SI{500}{\milli\second}, so the \SI{20}{\milli\second} standard deviation for
+hexadecane means that the variation in retention time is only about
+\SI{10}{\percent} of the peak width. The relative standard deviations (RSD) of
+retention times were similar to those obtained in GC×GC\cite{Shellie2002}.
 
@@
 \hline
-Dodecane & 73 & 5.069 & 0.0231 & 0.456\\
-Hexadecane & 73 & 6.584 & 0.0516 & 0.784\\
+Dodecane & 73 & 5.07 & 0.023 & 0.46\\
+Hexadecane & 73 & 6.58 & 0.052 & 0.78\\
 \end{tabular}
@@
 \begin{figure}
-\includegraphics[width=8.5cm]{./Figures/Interpretation.png}%
+\includegraphics[width=\textwidth]{./Figures/Interpretation.png}%
 
@@
 Prof. Walter Meyer of the Department of Physics at the University of Pretoria
-supplied the idea for the electronics that measure the resistance of the
-stainless steel heating tube. Nico van Vuuren machined the T-piece blocks and
-their mounting rails. We thank Restek for the generous donation of the packed
-silica columns. Reinhardt Heymans from FLIR Systems recorded the thermal images
-at no cost. David Masemula kept the laboratory supplied with consumables.
+supplied the idea for the resistance-measuring electronic circuit. Nico van
+Vuuren machined the T-piece blocks and their mounting rails. We thank Restek for
+the generous donation of the packed silica columns. Reinhardt Heymans from FLIR
+Systems recorded the thermal images at no cost. David Masemula kept the
+laboratory supplied with consumables.
 

### 2020-01-04 Journal/ResponseLetter.tex
Final version as submitted after adding response to reviewers.

% Title:    A LaTeX Template For Responses To a Referees' Reports
% Author:   Petr Zemek <s3rvac@gmail.com>
% Homepage: https://blog.petrzemek.net/2016/07/17/latex-template-for-responses-to-referees-reports/
% License:  CC BY 4.0 (https://creativecommons.org/licenses/by/4.0/)
\documentclass[10pt]{article}

% Allow Unicode input (alternatively, you can use XeLaTeX or LuaLaTeX)
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{eurosym}
\usepackage{textcomp}

\usepackage{microtype,xparse,tcolorbox}
\newenvironment{reviewer-comment }{}{}
\tcbuselibrary{skins}
\tcolorboxenvironment{reviewer-comment }{empty,
  left = 1em, top = 1ex, bottom = 1ex,
  borderline west = {2pt} {0pt} {black!20},
}
\ExplSyntaxOn
\NewDocumentEnvironment {response} { +m O{black!20} } {
  \IfValueT {#1} {
    \begin{reviewer-comment~}
      \setlength\parindent{2em}
      \noindent
      \ttfamily #1
    \end{reviewer-comment~}
  }
  \par\noindent\ignorespaces
} { \bigskip\par }

\NewDocumentCommand \Reviewer { m } {
  \section*{Comments~by~Reviewer~#1}
}
\ExplSyntaxOff
\AtBeginDocument{\maketitle\thispagestyle{empty}\noindent}

% You can get probably get rid of these definitions:
\newcommand\meta[1]{$\langle\hbox{#1}\rangle$}
\newcommand\PaperTitle[1]{``\textit{#1}''}

\title{Response letter of \meta{RSI19-AR-01677} \\
  Based on the Referees' Report}
\author{D. Malan \and S.J. van der Walt \and E.R. Rohwer}
\date{\today}

\begin{document}

\noindent
\textbf{Chin-Tu Chen}\\
\textbf{Associate Editor}\\
\textbf{Review of Scientific Instruments}

\medskip

\begin{quote}
Revision of the paper \meta{RSI19-AR-01677} submitted to the Review of
Scientific Instruments, entitled \PaperTitle{A high-repetition-rate, fast
temperature programmed gas chromatograph and its on-line coupling to a
supercritical fluid chromatograph (SFC×GC)}, based on the referees' report.
\end{quote}

\medskip

\noindent
Dear Chin-Tu Chen:

Thank you for your email dated 7 November 2019 enclosing the reviewers’ comments. We
have carefully reviewed the comments and have revised the manuscript accordingly. Our
responses are given in a point-by-point manner below.

We hope the revised version is now suitable for publication and look forward to hearing from you
in due course.

\vspace{\baselineskip}

\noindent
Yours sincerely,\\
D. Malan\\
Department of Chemistry\\
University of Pretoria

\Reviewer{\#1}
\begin{response}{Abstract, last line: the sentence fragment 'separating fatty information" needs revision.
	}
 	The sentence was revised and clarified.
\end{response}

\begin{response}{p3, orthogonal and general elution problem. In trying to wrap
my head around this argument, I can't help but think that despite their comment
about GC×GC wrap-around, it does seem that this would be even more of a problem
in their current setup or those using LC-GC. The authors miss the opportunity to
justify the need for fast temperature programmed GC in their second dimension.
Perhaps laying their arguments out in more detail here would be useful.
} 
The problem with the vagueness of the argument was identified. The paragraphs
were changed to clarify how the general elution problem applies to
multidimensional chromatography, and to emphasize that SFC×GC demands
temperature programming in the GC dimension.
\end{response}

\begin{response}{p6 last line, sentence structure needs revision.
	}  The sentence was revised and clarified.
\end{response}

\begin{response}{p7, description of the connection blocks. Refer the reader to see Figure 1 here. 
	}  A reference to Figure 1 was added.
\end{response}

\begin{response}{Also, singular-plural confusion in :"These blocks fulfilled three roles: It (1) sealed ... "
	}  
	The confusion was cleared up. 
\end{response}

\begin{response}{Figure 1. It is not clear from the drawing that the cryogenic
coolant actually enters the heater tube. While the dimensions of the drawing are
perhaps selected to be according to scale, the reader would benefit from a
little artistic liberty here. (g) "electrical connection" is a little vague.
	} The figure was changed to add a schematic diagram that illustrate the coolant
	flow, and the caption was clarified.
\end{response}

\begin{response}{p9. Reference resistor and ballast resistor. What are the
dimensions of the wires used to construct these resistors? What is the
resistance of the ballast? 
	} 
	The requested details were added, as well as a figure that shows the construction of the relevant resistors.
\end{response}

\begin{response}{p13, A. Heating uniformity. Text says video is shown in
Figure3. Figure 3 is a screen capture of the video shown in Supplemental
Material. Correct accordingly.
	}
	We recognize the inaccuracy, and the text was corrected. 
\end{response}

\begin{response}{ p13. Gradients by cooling. Not sure how this statement
accurately reflects the repeated heating cycles shown in Figure 4. Further
information and a more detailed description of Figure 4 is required. Does the
difference between the two calibration points along the length of the column (33
and 66 cm) increase with temperature? 
	}  
	The discussion on the gradients measured by thermocouple was revised and expanded for greater clarity. 
\end{response}

\begin{response}{Figure 5. Explain in the heading the blue and red lines.
	}  
	The caption was revised with a better description that includes an explanation of the colours.
\end{response}

\begin{response}{Figure 2. Can be improved by showing more details of the
circuit, rather than just three resistors in series.
	}  The figure was replaced by a more detailed one, and the description in the text was adapted to match the figure.   
\end{response}

\begin{response}{A few references appear incomplete. e.g. 17 and 29.}  
	The bibliography was reviewed and all the incomplete references were updated.
\end{response}

\Reviewer{\#2}

\begin{response}{p1 Abstract, sentence change: We demonstrate the fast
chromatograph by separating fatty acid methyl esters by carbon number, which
would be useful in the food and biodiesel industries.
	}  
	The sentence was clarified. 
\end{response}

\begin{response}{p2: This concept is called comprehensively coupled
chromatography. For example, in comprehensively coupled gas chromatography
(GC×GC). Confirm correct nomenclature in as published by Marriot in LCGC 2012.
	} We thank the reviewers for drawing attention to using correct nomenclature. We
	revised the manuscript to ensure the recommended nomenclature was used throughout.
\end{response}

\begin{response}{p2 Sentence change: The use of narrow-bore columns and thin
films reduce run times by improving mass transfer between the mobile and
stationary phases, resulting in analytes spending more time in the mobile phase
allowing shorter retention times.

	} We agree that the sentence needed clarification, but disagree with the
	explanation. Improved mass transfer does not allow analytes to spend more time
	in the mobile phase, but it does reduce peak broadening.  The sentence was
	revised thusly: \textit{Typically, short columns and high carrier flows rates
	are used, which reduce retention times by reducing void times. Resolution can be
	maintained at even higher gas flows by using narrow-bore columns and thin films:
	these improve the mass transfer rate between the mobile and stationary phases,
	which reduces peak broadening by bringing the analyte exchange between the
	phases closer to equilibrium at higher-than-optimum carrier gas velocities.}

\end{response}

\begin{response}{p3 sentence change: it becomes unlikely that one set of
acceptable operating conditions (temperature, flow and stationary phase) will
give acceptable (fast enough and with adequate resolution) separation in both
dimensions.
	}  This sentence was revised as part of general improvement in the argument.
	(See Reviewer 1, comment ``p.3'')
\end{response}

\begin{response}{p3 sentence change: so late that the next modulation period has
already started before its elution and the peak only appears on the next 2D
chromatogram 
	}  The sentence was revised as suggested.
\end{response}

\begin{response}{p3 sentence change: If wraparound is a problem in GC×GC, it
becomes inevitable in SFC×GC since the first dimension (SFC) does not normally
separate compounds in a way that correlates with vapour pressure.
	}  This sentence was improved by revising the paragraph. 
\end{response}

\begin{response}{p5 sentence change: The Zip ScienticTM solution operates by forced convection.}  
	The sentence was changed to the suggested one. 
\end{response}

\begin{response}{p5: sentence change: In our case we applied it as a fast second
dimension separation, comprehensively coupled to a supercritical fluid
chromatograph.
	}  The sentence was changed to the suggested one. 
\end{response}

\begin{response}{p6 clarification: clarify what type of static restriction was
used.
	}  The description of the static restrictor was improved. 
\end{response}

\begin{response}{p6: sentence change: the stop valve opens and the SFC eluate
exits the restrictor into the hot splitless inlet of the GC, where it evaporates
and is transported onto the GC column.
	}  This sentence was improved by rewriting the paragraph. 
\end{response}

\begin{response}{p6: sentence change: which of course means the start of the
temperature program, which desorbs the analyteS trapped on the head of the cold
column.
	}  This sentence was improved by rewriting the paragraph.
\end{response}

\begin{response}{p7: sentence change: The split vent valve was disconnected from
the gas chromatograph CONTROL and CONNECTED TO the control computer described
below 
	}  The sentence was changed to the suggested one. 
\end{response}

\begin{response}{p10: Figure 2: Figure do not contain that much detail and may
be omitted.
	}  The figure was replace by a more detailed one, and the text adapted to match
	the figure. (See Reviewer 1, comment ``Figure 2'')
\end{response}

\begin{response}{p12: abbreviation: LabVIEW 7.1TM (National Instruments). This
abbreviation was used earlier p10 and should be clarified there.
	}  We recognize the oversight and corrected it.
\end{response}

\begin{response}{p15: sentence change: In the instrument presented here, THE
power was limited by the voltage output range of the DAC of the data acquisition
board, and not by the power of the heater.
	}  The sentence was replaced by the suggested one.
\end{response}

\end{document}

### 2020-01-04 Journal/DecisionLetter.tex
Final version as submitted after adding response to reviewers.

Email
Manuscript #	RSI19-AR-01677
Title	A high-repetition-rate, fast temperature programmed gas chromatograph and its on-line coupling to a supercritical fluid chromatograph (SFC×GC)
Corresponding Author	Egmont R Rohwer (University of Pretoria Department of Chemistry)
Date:	07-Nov-2019 19:42:33
Last Sent:	07-Nov-2019 19:42:33
Created By:	Redacted
From:	rsi-edoffice@aip.org
To:	egmont.rohwer@up.ac.za
Subject:	RSI: MS #RSI19-AR-01677 Decision Letter
Email	Dear Prof. Rohwer

Thank you for submitting your manuscript, referenced below, to Review of Scientific Instruments for consideration.

"A high-repetition-rate, fast temperature programmed gas chromatograph and its on-line coupling to a supercritical fluid chromatograph (SFC×GC)"

RSI19-AR-01677

Your manuscript has been reviewed, and I am pleased to inform you that it has received a favorable recommendation from the reviewers. Please see the report below, which lists the comments of the reviewers and myself. It contains suggestions for minor revisions that I believe will improve your paper.

Please make the appropriate changes and upload your revised manuscript files using the link below. When uploading your revised manuscript, you should:

- Indicate in your response letter how the manuscript has been revised to
address the points raised by the reviewers. For comments or suggestions with
which you do not agree, please provide a rebuttal.

- Include your manuscript number in your response letter.

- Upload your revised manuscript file in .doc, .docx, or .tex format with no
highlighted or marked text. (You will have the option to upload a separate,
marked-up version of your manuscript.)

- Upload separate figure files for each cited figure in EPS (preferred), PS,
TIFF (.tif), PDF, or JPEG (.jpg) format. For multi-panel figures, please upload
a single file containing all figure panels.

Click on the following link to submit your revised manuscript:

Link Not Available

Your revised manuscript is due 06-Jan-2020. Please submit your revised manuscript promptly. A manuscript returned after 06-Jan-2020 will be regarded as a new submission and will be assigned a new submission date. If that is required, please refer to your previous submission (include the previous manuscript number) in the cover letter.

Sincerely,

Chin-Tu Chen
Associate Editor
Review of Scientific Instruments

------------------------------------------------------------------------------
Manuscript #RSI19-AR-01677:

Editor's Comments:
Please review and consider carefully the critiques provided and issues raised by the two reviewers, and modify and improve your manuscript accordingly.
When you resubmit your revised paper, please include your point-to-point response to these critiques and issues.
-- CT Chen

Reviewer Comments:
Reviewer #1 Evaluations:
Recommendation: Publish after minor revision
Technically sound: Y
New ideas: Y
Just a variation of known device or technique: N
Appropriate journal: Y
Proper context with related work: Y
Clear explanation: Y
Adequate references: Y
Suitable title: Y
Adequate abstract: Y
Significant numerical quantities: Y
Clear figures with captions: Y
Excessive text or figures: Y
English satisfactory: Y
Regular Article vs Note: Regular Article

Reviewer #1 (Remarks):

The manuscript describes the design and construction of a novel high-repetition rate, resistively-heated, and actively-cooled programmed gas chromatograph, and its implementation as a second dimension in comprehensive multidimensional chromatography. The chromatographic arrangement is different from typical comprehensive separations in that the polar separation precedes the volatility separation. The authors do an excellent job of introducing the topic to a non-specialist audience, almost to a fault, and the manuscript could perhaps be a little more concise throughout.
While the GC is described as part of an SFCxGC system, its design would lend itself to other applications such as portable and fast GC for example in in-situ analyses.
While the design is described in sufficient detail, in some instances additional information could be provided and a few other corrections are suggested below.

Abstract, last line: the sentence fragment 'separating fatty information" needs revision.

p3, orthogonal and general elution problem. In trying to wrap my head around this argument, I can't help but think that despite their comment about GCxGC wrap-around, it does seem that this would be even more of a problem in their current setup or those using LC-GC. The authors miss the opportunity to justify the need for fast temperature programmed GC in their second dimension. Perhaps laying their arguments out in more detail here would be useful.

p6 last line, sentence structure needs revision.

p7, description of the connection blocks. Refer the reader to see Figure 1 here. Also, singular-plural confusion in :"These blocks fulfilled three roles: It (1) sealed ... "
Figure 1. It is not clear from the drawing that the cryogenic coolant actually enters the heater tube. While the dimensions of the drawing are perhaps selected to be according to scale, the reader would benefit from a little artistic liberty here.
(g) "electrical connection" is a little vague.

p9. Reference resistor and ballast resistor. What are the dimensions of the wires used to construct these resistors? What is the resistance of the ballast?

p13, A. Heating uniformity. Text says video is shown in Figure3. Figure 3 is a screen capture of the video shown in Supplemental Material. Correct accordingly.
p13. Gradients by cooling. Not sure how this statement accurately reflects the repeated heating cycles shown in Figure 4. Further information and a more detailed description of Figure 4 is required. Does the difference between the two calibration points along the length of the column (33 and 66 cm) increase with temperature?

Figure 5. Explain in the heading the blue and red lines.

Figure 2. Can be improved by showing more details of the circuit, rather than just three resistors in series.

A few references appear incomplete. e.g. 17 and 29.

Reviewer #2 Evaluations:
Recommendation: Publish after minor revision
Technically sound: Y
New ideas: Y
Just a variation of known device or technique: N
Appropriate journal: Y
Proper context with related work: Y
Clear explanation: Y
Adequate references: Y
Suitable title: Y
Adequate abstract: Y
Significant numerical quantities: Y
Clear figures with captions: Y
Excessive text or figures: Y
English satisfactory: Y
Regular Article vs Note: Regular Article

Reviewer #2 (Remarks):

The highly repetitive fast GC for the use in 2D separations is very valuable. The use of this in SFCxGC allows for a the application and testing of a wide variety of column and selectivity combinations. The ease of column change in the 2nd dimension becomes important during method development, however, changing columns for varying selectivity in the 1st dimension (SFC) can be done easily. The authors have gone to great lengths to ensure that the heating, cooling and other aspects are repeatable and fast. The combination with SFC, as in this paper, will allow for a wide variety of application areas.

Proposed changes:
p1 Abstract, sentence change: We demonstrate the fast chromatograph by separating fatty acid methyl esters by carbon number, which would be useful in the food and biodiesel industries.

p2: This concept is called comprehensively coupled chromatography. For example, in comprehensively coupled gas chromatography (GCxGC). Confirm correct nomenclature in as published by Marriot in LCGC 2012.

p2 Sentence change: The use of narrow-bore columns and thin films reduce run times by improving mass transfer between the mobile and stationary phases, resulting in analytes spending more time in the mobile phase allowing shorter retention times.

p3 sentence change: it becomes unlikely that one set of acceptable operating conditions (temperature, flow and stationary phase) will give acceptable (fast enough and with adequate resolution) separation in both dimensions.

p3 sentence change: so late that the next modulation period has already started before its elution and the peak only appears on the next 2D chromatogram

p3 sentence change: If wraparound is a problem in GCxGC, it becomes inevitable in SFCxGC since the first dimension (SFC) does not normally separate compounds in a way that correlates with vapour pressure.

p5 sentence change: The Zip ScienticTM solution operates by forced convection.

p5: sentence change: In our case we applied it as a fast second dimension separation, comprehensively coupled to a supercritical fluid chromatograph.

p6 clarification: clarify what type of static restriction was used.

p6: sentence change: the stop valve opens and the SFC eluate exits the restrictor into the hot splitless inlet of the GC, where it evaporates and is transported onto the GC column.

p6: sentence change: which of course means the start of the temperature program, which desorbs the analyteS trapped on the head of the cold column.

p7: sentence change: The split vent valve was disconnected from the gas chromatograph CONTROL and CONNECTED TO the control computer described below

p10: Figure 2: Figure do not contain that much detail and may be omitted.

p12: abbreviation: LabVIEW 7.1TM (National Instruments). This abbreviation was used earlier p10 and should be clarified there.

p15: sentence change: In the instrument presented here, THE power was limited by the voltage output range of the DAC of the data acquisition board, and not by the power of the heater.

------------------------------------------------------------------------------

### 2020-01-04 document.tex
Final version as submitted after adding response to reviewers.

@@
 
-\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for checking your page length
+\documentclass[aip,rsi,preprint]{revtex4-2} % for checking your page length
 %\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes
@@
 We present a fast gas chromatographic system that can be used as a second
-dimension in comprehensive (supercritical fluid × gas) chromatography (SFC×GC).
-The temperature of the short (1 metre long) capillary column is controlled by a
-resistively heated coaxial stainless-steel tube. The electrical resistance and
-therefore temperature of the stainless-steel tube is measured by continuous
-monitoring of the current/voltage ratio. Highly repeatable heating rates of up
-to \SI{2100}{\celsius\per\minute} (\SI{35}{\celsius\per\second}) are obtained,
-which should be high enough for the most demanding fast chromatograms. To reduce
-the cooling time between temperature programs the column is cooled by injecting
-evaporating carbon dioxide into the space between the coaxial heater and the
-column. This gives cooling rates of \SI{5100}{\celsius\per\minute}
-(\SI{85}{\celsius\per\minute}) which allows quick succession of temperature
-programs. More repeatable heating profiles with stable GC retention times
-together with faster cooling are significant improvements on previous SFC×GC
-systems. Cycle times of four gas chromatograms per minute could readily be
-achieved, which allows efficient coupling to high-resolution stop-flow SFC in
-the first dimension. We demonstrate the fast chromatograph by separating fatty
+dimension in comprehensive two-dimensional (supercritical fluid × gas)
+chromatography (SFC×GC). The temperature of the short (1 metre long) capillary
+column is controlled by a resistively heated coaxial stainless-steel tube. The
+electrical resistance and therefore temperature of the stainless-steel tube is
+measured by continuous monitoring of the current/voltage ratio. Highly
+repeatable heating rates of up to \SI{2100}{\celsius\per\minute}
+(\SI{35}{\celsius\per\second}) are obtained, which should be high enough for the
+most demanding fast chromatograms. To reduce the cooling time between
+temperature programs the column is cooled by injecting evaporating carbon
+dioxide into the space between the coaxial heater and the column. This gives
+cooling rates of \SI{5100}{\celsius\per\minute} (\SI{85}{\celsius\per\second})
+which allows quick succession of temperature programs. More repeatable heating
+profiles with stable GC retention times together with faster cooling are
+significant improvements on previous SFC×GC systems. Cycle times of four gas
+chromatograms per minute could readily be achieved, which allows efficient
+coupling to high-resolution stop-flow SFC in the first dimension. We demonstrate
+the fast chromatograph by separating fatty acid methyl esters, yielding
 information which would be useful in the food and biodiesel industries.
@@
 Chromatography as an analytical technique is notoriously slow, compared to, say,
-some spectroscopic techniques.
-
-While it is of interest to (especially high-throughput) laboratories to reduce
-run times, at some point the faster chromatography starts outstripping the
-sample preparation capacity. Once the chromatographic run duration approaches
-the time it takes to prepare the sample, faster chromatography will not improve
-the sample throughput. Technology development in fast chromatography is
-therefore driven not by conventional injection-based chromatography, but by
-applications where no sample preparation is necessary and rapid results are
-needed.
+some spectroscopic techniques. While it is of interest to (especially
+high-throughput) laboratories to reduce run times, at some point the faster
+chromatography starts outstripping the sample preparation capacity. Once the
+chromatographic run duration approaches the time it takes to prepare the sample,
+faster chromatography will not improve the sample throughput. Technology
+development in fast chromatography is therefore driven not by conventional
+injection-based chromatography, but by applications where no sample preparation
+is necessary and rapid results are needed.
 
@@
 fractions of eluate from chromatographic separations. This concept is called
-\textit{comprehensively coupled chromatography}. For example, in comprehensively
-coupled gas chromatography (GC×GC), fractions of a conventional gas
+\textit{comprehensive two-dimensional chromatography}. For example, in comprehensive
+two-dimensional gas chromatography (GC×GC), fractions of a conventional gas
 chromatographic run are collected by a \textit{modulator} and then admitted to a
@@
 developed\cite*{Cramers1999,Korytar2002}. Typically, short columns and high
-carrier flows rates are used, which reduce retention times by reducing the
-void time. The use of narrow-bore columns and thin films reduce run times by
-improving mass transfer between the mobile and stationary phases, allowing
-higher linear flow rates of the carrier gas.
-
-Comprehensively coupled chromatography depends on \textit{orthogonality}: the
-second dimension ($^2$D) separation must have a different mechanism than that of
-the first dimension ($^1$D) separation\cite*{Giddings1995,Camenzuli2014}. The
-higher the orthogonality, the better the \textit{separation space} offered by
-the system. The different separation mechanisms that determine orthogonality are
-usually provided by the different stationary phases offered by column
-manufacturers, but it is also possible to use a different form of chromatography
-as a first dimension: liquid chromatography has been used as a first dimension
-in LC×GC\cite{Koning2004}, and in our laboratory we are developing
-SFC×GC instrumentation\cite{Venter2004}.
+carrier flows rates are used, which reduce retention times by reducing void
+times. Resolution can be maintained at even higher gas flows by using
+narrow-bore columns and thin films: these improve the mass transfer rate between
+the mobile and stationary phases, which reduces peak broadening by bringing the
+analyte exchange between the phases closer to equilibrium at higher-than-optimum
+carrier gas velocities.
+
+Comprehensive two-dimensional chromatography depends on \textit{orthogonality}:
+the second dimension ($^2$D) separation must have a different mechanism than
+that of the first dimension ($^1$D)
+separation\cite*{Giddings1995,Camenzuli2014}. The higher the orthogonality, the
+better the \textit{separation space} offered by the system. In GC×GC the
+different separation mechanisms that determine orthogonality are usually
+provided by the different stationary phases offered by column manufacturers, but
+it is also possible to use a different form of chromatography as a first
+dimension: liquid chromatography has been used as a first dimension in
+LC×GC\cite{Koning2004}, and in our laboratory we are developing SFC×GC
+instrumentation\cite{Venter2004}.
 
 If a chromatographic $^2$D separation is highly orthogonal to the $^1$D
-separation, then we will run into the \textit{general elution
-problem}\cite{Skoog2007}: it becomes unlikely that one set of acceptable
-operating conditions (temperature, flow and stationary phase) will give
-acceptable (fast enough and with adequate resolution) separation.
-
-In GC×GC as it is practised today, this has become a real problem.
-\textit{Wraparound} is a well-known phenomenon in
-GC×GC\cite{Dalluege2003}. Wraparound happens when a peak or peaks elute
+separation, then the $^2$D separation will run into the \textit{general elution
+problem}\cite{Skoog2007}: the higher the orthogonality, the more diverse the
+compounds found in each $^1$D fraction, and it becomes increasingly unlikely
+that one set of acceptable operating conditions (temperature, flow and
+stationary phase) will an give acceptable (fast enough and with adequate
+resolution) $^2$D separation. In GC×GC as it is practised today this has become
+a real problem, known as \textit{wraparound}, a well-known
+phenomenon\cite{Dalluege2003}. Wraparound happens when a peak or peaks elute
 `late' on the second dimension, so late that the next modulation period has
-already started before its elution and the peak appears on the next $^2$D
-chromatogram.
-
-% There are ways to avoid or ignore wraparound, but using gradient elution in
-% the second dimension would, in principle, prevent all wraparound.
-
-If wraparound is a problem in GC×GC, it becomes inevitable in
-SFC×GC. The first dimension (SFC) does not normally separate compounds in
-a way that correlates with vapour pressure. Indeed, SFC is particularly good in
-performing group-type separations\cite{Venter1999}, where compounds with a wide
-range of boiling points elute together.
-
-\subsection{Column heating for gas chromatography}
+already started before its elution and the peak only appears on the next $^2$D
+chromatogram. Careful interpretation of 2D chromatograms can identify which
+peaks can be attributed to wraparound, and adjusting some parameters might
+mitigate the problem.
+
+If the general elution problem causes the phenomenon of wraparound in GC×GC,
+where the compounds found in $^1$D fractions have a relatively narrow boiling
+point range, it will cause much greater problems in SFC×GC, since the first
+dimension (SFC) does not normally separate compounds in a way that correlates
+with vapour pressure. Indeed, SFC is particularly good in performing group-type
+separations\cite{Venter1999}, where compounds with a wide range of boiling
+points elute together. Therefore, in SFC×GC we can expect compounds with a wide
+range of boiling points in each $^1$D (SFC) fraction, and the general elution
+problem makes it unlikely that an isothermal $^2$D (GC) run will provide an
+acceptable separation. This is why successful SFC×GC demands temperature
+programming in the GC dimension.
+
+\subsection{Fast column heating for GC}
 
@@
 programming, \textit{i.e.} increasing the temperature of the column throughout
-the duration of the chromatograpic run. Temperature programming decreases the
+the duration of the chromatographic run. Temperature programming decreases the
 retention times of late-eluting analytes without sacrificing the resolution of
@@
 
-\subsection{Cooling of the GC column}
+\subsection{Fast column cooling for GC}
 
@@
 There have been attempts to improve the cooling rate of air baths.
-
 Agilent\texttrademark{} markets a `low thermal mass' column, which includes a
@@
 been reported\cite{Luong2006}. These columns are available with only a limited
-range of stationary phases.
-
-The Zip Scientific\texttrademark{} solution is forced convection. Their
-`GC-Chaser' system uses a blast of (chilled) room air to the
-GC oven to cool it down after each GC run, allowing the use of conventional
-fused silica columns. In an example\cite{ZipScientific2008} it reduces cooling
-time from 16 minutes to 7 minutes. Although this can significantly decrease the
-cost per analysis in a high-throughput laboratory, the cooling is not fast
-enough for 2D chromatography.
-
-The EZ Flash\texttrademark{} system uses a coaxial resistive heating system,
-which allows the column to cool down ballistically. Reports from the literature
-claims cool-down periods of 30 seconds\cite{Dalluege1999}.
-
-The Valco FTP-200 fast temperature programmer\cite{VICIAGI2019} (Valco
-Instruments Co. Inc.) uses a small, optional fan to cool down the columns.
+range of stationary phases. The Zip Scientific\texttrademark{} solution operates
+by forced convection. Their `GC-Chaser' system uses a blast of (chilled) room
+air to the GC oven to cool it down after each GC run, allowing the use of
+conventional fused silica columns. In an example\cite{ZipScientific2008} it
+reduces cooling time from \SI{16}{\minute} to \SI{7}{\minute}. Although this can
+significantly decrease the cost per analysis in a high-throughput laboratory,
+the cooling is not fast enough for 2D chromatography. The EZ
+Flash\texttrademark{} system uses a coaxial resistive heating system, which
+allows the column to cool down ballistically. Reports from the literature claims
+cool-down periods of \SI{30}{\second} \cite{Dalluege1999}. The Valco FTP-200
+fast temperature programmer\cite{VICIAGI2019} (Valco Instruments Co. Inc.) uses
+a small, optional fan to cool down the columns.
 
@@
 each run, using large quantities of coolant in the process. The resistively
-heated column cooling required 30 seconds to get back to the starting
+heated column cooling required \SI{30}{\second} to get back to the starting
 temperature in this cool environment. We estimate that a single SFC×GC run
-consumed an unacceptable 15 kg of carbon dioxide coolant.
+consumed an unacceptable \SI{15}{\kilo\gram} of carbon dioxide coolant.
 
@@
 fast chromatograms are needed in rapid succession, for example in process
-control. In our case we applied it as a $^2$D column comprehensively coupled to
-a supercritical fluid chromatograph.
+control. In our case we applied it as a fast second dimension separation,
+comprehensively coupled to a supercritical fluid chromatograph.
 
@@
 potential biodiesel feedstock. The fast GC separation was highly orthogonal to
-the $^1$D separation on SFC, showcasing this type of comprehensively coupled
-chromatography. An easily interpretable 2D separation was obtained, with run
-times similar to the total run times required by official methods for the
-determination of fatty acid profiles.
+the $^1$D separation on SFC, showcasing this type of comprehensive
+two-dimensional chromatography. An easily interpretable 2D separation was
+obtained, with run times similar to the total run times required by official GC
+methods for the determination of fatty acid profiles.
 
@@
 For better understanding of subsequent detail, a description of the cycle of the
-SFC×GC is appropriate.
-
-The SFC subsystem runs in stop-flow mode. The eluate of the SFC passes through a
-stop valve and a static capillary restrictor. The end of the restrictor is 
-inserted through the septum into the hot inlet of the GC.
-
-After the sample is injected, the SFC runs for an optional uninterrupted period,
-usually briefer than the void time. No data is collected during this time. Then
-the stop valve closes, and the cooling system activates to cool the GC column.
-Once the column is at the set temperature, the stop valve opens and the SFC
-eluate exits the restrictor into the hot splitless inlet of the GC, where it
-evaporates and is transported on to the column. The vapor-phase material
-is trapped in the cold stationary phase. Once the desired amount
-of the SFC eluate has been collected, the stop valve closes. Some time is
-allowed to pass so that the last of the evaporated SFC eluate flushes into the
-column. Then the split vent of the GC inlet opens for a short period, which
-vents excess carbon dioxide to the atmosphere. This normalizes the pressure in
-the inlet (having been raised  by the high flow rate of CO$_2$ from the SFC) and
-allows the carbon dioxide to be replaced by the pressure-controlled hydrogen
-carrier gas. Once the split vent closes the GC run starts, which of course means
-the start of the temperature program, which desorbs the analyte trapped on the
-head of the cold column. At the end of the GC run, the cooling process starts,
-cooling the column in a second or two. The next cycle then starts, marked by the
-opening of SFC the stop valve.
+SFC×GC is appropriate. The SFC subsystem runs in stop-flow mode. The eluate of
+the SFC passes through a stop valve and a static linear capillary restrictor.
+The end of the restrictor is inserted through the septum into the hot inlet of
+the GC. After the sample is injected, the SFC runs for an optional uninterrupted
+period, usually briefer than the void time. No data is collected during this
+time. Then the stop valve closes, and the cooling system activates to cool the
+GC column. Once the column is at the set temperature, the stop valve opens and
+the SFC eluate exits the restrictor into the hot splitless inlet of the GC,
+where it evaporates instantly. The vapour-phase material is swept from the inlet
+onto the column where it is trapped in the cold stationary phase. Once the
+desired amount of the SFC eluate has been collected, the stop valve closes and
+some time is allowed to elapse so that the last of the evaporated SFC eluate can
+be flushed into the column. Then the split vent of the GC inlet opens for a
+short period to vent excess carbon dioxide to the atmosphere. This normalizes
+the pressure in the inlet (having been raised  by the high flow rate of CO$_2$
+from the SFC) and allows the carbon dioxide to be replaced by the
+pressure-controlled hydrogen carrier gas. The closing of the split vent marks
+the start of the GC run, which of course means the start of the temperature
+program. Under control of the temperature program the analytes trapped on the
+head of the cold column desorb, migrate, separate, elute, and
+are detected. The end of the temperature program marks the end of the GC run,
+and the GC column is cooled to prepare for trapping the next fraction.
 
@@
 The short-cycle fast gas chromatograph was built into a modified
-Varian\texttrademark{} 3300 gas chromatograph.
-
-The inlet was an unmodified Varian\texttrademark{} 1075 split/splitless inlet.
-The temperature control of the inlet was by the original electronics, controlled
-from the Varian 3300 front panel. The split vent valve was disconnected from the
-gas chromatograph and controlled from the control computer described below.
+Varian\texttrademark{} 3300 gas chromatograph. The inlet was a
+Varian\texttrademark{} 1075 split/splitless inlet. The temperature control of
+the inlet was by the original electronics, controlled from the Varian 3300 front
+panel. The split vent valve was disconnected from the gas chromatograph control
+and connected to the control computer described below.
 
 The detector was an unmodified Varian\texttrademark{} 3300 flame ionization
-detector (FID). The temperature of the detector was controlled by the original
+detector (FID). The temperature of the detector was regulated by the original
 electronics, controlled from the front panel. The detector bias voltage was
@@
 
-The coaxial heater was made of a 940 mm length of stainless steel (SAE 304
-grade), obtained from MIFAM (Milanówek, Poland). It had an outside diameter of
-1.06 mm and an inside diameter of 0.80 mm.
-
-The ends of the coaxial heater tube terminated in two identical, specially
-designed T-piece blocks. These blocks fulfilled three roles: It (1) sealed the
-coaxial tube to contain coolant, (2) allowed electrical connection to the
-coaxial heater, and (3) acted as a heated transfer line between the column and
-the detector and inlet.
-
-The T-piece blocks were machined from brass. The stainless-steel tube of the
-coaxial heater was brazed onto the block. The cooling CO$_2$ was let in from one
-side, and on the opposite side a thermocouple probe inserted into a blind hole
-measured the temperature of the block. A micro-union using a metal ferrule
-(Restek\texttrademark{} SilTite $\mu$-Union Connectors), brazed to the block,
-was used to seal the capillary column. An electrical contact was added, to which
-an electrical conductor could be soft-soldered. Four holes through the length of
-the block allowed the fitting of four 220V, 100 W heater cartridges (Hotset),
-providing each of the two blocks 400W of heating.
+The coaxial heater was made of a \SI{940}{\milli\metre} length of stainless
+steel (SAE 304 grade), obtained from MIFAM (Milanówek, Poland). It had an
+outside diameter of \SI{1.06}{\milli\metre} and an inside diameter of
+\SI{0.80}{\milli\metre}. The ends of the coaxial heater tube terminated in two
+identical, specially designed T-piece blocks, machined from brass (See Figure
+\ref{fig:Manifold}). These blocks fulfilled three roles:
+They (1) sealed the coaxial tube to contain coolant, (2) allowed electrical
+connection to the coaxial heater, and (3) acted as a heated transfer line
+between the column and the detector and inlet. Each end of the stainless-steel
+tube of the coaxial heater was brazed onto a block. The CO$_2$ coolant passed
+through one side, and on the opposite side a thermocouple probe inserted into a
+blind hole measured the temperature of the block. An electrical contact was
+added, to which an electrical conductor could be soft-soldered. Four holes
+through the width of the block allowed the fitting of four \SI{220}{\volt},
+\SI{100}{\watt} heater cartridges (Hotset), providing each of the two blocks
+\SI{400}{\watt} of heating.  The chromatographic capillary column entered the
+T-piece block via the bottom port with the coaxial heater tube and passed out
+through the top port (where a micro-union using a metal ferrule
+(Restek\texttrademark{} SilTite $\mu$-Union Connectors) brazed to the block
+created a seal to contain the coolant) and into the inlet or detector.
 
 \begin{figure}
-	\includegraphics[width=\textwidth]{./Figures/Cutaway_with_symbols.png}
-	\caption["The T-piece block"]{A cutaway diagram of the inlet/outlet outlet T-piece blocks, showing the (a) cryogenic coolant inlet/outlet, (b) the coaxial heater, (c) the capillary column, (d) the mico-union seal, (e) the cartridge heater socket, (f) the thermocouple socket, and (g) the electrical connection.}%
+	\includegraphics[width=\textwidth]{T-Piece.eps}
+
+\caption["The T-piece block"]{Left: A cutaway diagram of the inlet/outlet outlet
+T-piece blocks with all the parts to scale, showing (a) the cryogenic coolant
+inlet/outlet, (b) the coaxial heater, (c) the capillary column, (d) the
+micro-union seal, (e) the cartridge heater socket, (f) the thermocouple socket,
+and (g) the connector to which the power feed conductor was soft-soldered.
+Right: A schematic diagram showing the flow of the coolant through the T-piece
+block into the coaxial heater.}%
+
 	\label{fig:Manifold}
 \end{figure}
-
-The chromatographic column entered the T-piece block via the bottom port with the
-coaxial heater tube and passed out through the top port and into the inlet or
-detector. In the left-hand side of the T-piece block was the inlet or outlet port for the
-carbon dioxide coolant.
-
-%A blind hole on the right-hand side of the manifold mounted a thermocouple. The
-%temperature reported by the thermocouple was fed to control software, which
-%controlled the temperature of the manifold.
-
-Since the coaxial heater resistance measurement used a two-wire technique, the
-current-carrying circuit was made entirely of soldered joints to minimize stray
-resistance from developing in electrical connections.
 
@@
 The cryogenic carbon dioxide (Afrox, Tec (Wet)) was supplied from a cylinder
-equipped with a dip tube. It flowed to a coil heat exchanger bathed in a cold
-\SI{-5}{\celsius}) propylene glycol heat transfer fluid, which was mounted on
-top of the Varian GC. From the heat exchanger the carbon dioxide flowed down to
-the cryo shut-off valve (ASCO, RedHat brand). This arrangement ensured a supply
-of liquid CO$_2$ at the shut-off valve, without which some gaseous CO$_2$ might
-have to vent through the coaxial heater before the liquid CO$_2$ coolant could
-reach it. Downstream of the shut-of valve there was a 10-turn metering valve,
-which controlled the flow of carbon dioxide into the coaxial heater for
-evaporative cooling. At the outlet end of the coaxial heater the carbon dioxide
-escaped through the T-piece block into the atmosphere.
-
-The SFC subsystem consisted of five packed silica columns (150 mm × 4.6
-mm, 3 $\mu$m particles) (Restek, Pinnacle DB Silica) in series, a sample valve
-(VICI), and a stop valve (VICI). Carbon dioxide, (99.995 \% purity, Air
-Products) was supplied to a Varian 8500 piston pump. The inlet pressure of the
-SFC columns was controlled by a software proportional controller driving the
-stepper motor of the piston pump. The high pressure at the column exit was
-maintained by a fused silica capillary restrictor with an internal diameter of
+equipped with a dip tube. It flowed to a coil heat exchanger mounted on top of
+the Varian GC from where the carbon dioxide flowed down to the cryo shut-off
+valve (ASCO, RedHat brand). (The heat exchanger was bathed in a cold
+(\SI{-5}{\celsius}) propylene glycol heat transfer fluid.) This arrangement
+ensured a supply of liquid CO$_2$ at the shut-off valve, without which some
+gaseous CO$_2$ might have to vent through the coaxial heater before the liquid
+CO$_2$ coolant could reach it. Downstream of the shut-of valve a 10-turn
+metering valve controlled the flow of carbon dioxide into the coaxial heater. At
+the outlet end of the coaxial heater the carbon dioxide escaped through the
+T-piece block into the atmosphere.
+
+The SFC subsystem consisted of five packed silica columns
+(\SI{150}{\milli\metre} × \SI{4.6}{\milli\metre}, \SI{3}{\micro\metre}
+particles) (Restek, Pinnacle DB Silica) in series, a sample valve (VICI), and a
+stop valve (VICI). Carbon dioxide, (\SI{99.995}{\percent} purity, Air Products)
+was supplied to a Varian 8500 piston pump. The inlet pressure of the SFC columns
+was controlled by a software proportional controller driving the stepper motor
+of the piston pump. The high pressure at the column exit was maintained by a
+linear fused silica capillary restrictor with an internal diameter of
 \SI{0.050}{\milli\metre}, \SI{800}{\milli\metre} long.
@@
 The electronics for controlling the fast temperature programmed gas
-chromatograph and the SFC front-end was developed in-house.
-
-A controlled direct current was used to heat the coaxial heater. The heating
-circuit consisted of the coaxial heater in series with a reference resistor and
-a ballast resistor. The reference resistor was constructed out of parallel
-stainless-steel wires with an open construction to promote heat dissipation with
-the aim of keeping its temperature constant. The ballast resistor was of
-stainless-steel wire in a bifilar winding with an air core, to minimize
-electromagnetic interference and encourage heat dissipation.
+chromatograph and the SFC front-end was developed in-house. A controlled direct
+current was used to heat the coaxial heater. The heating circuit consisted of
+the coaxial heater in series with a reference resistor and a ballast resistor.
+The reference and ballast resistors were constructed from stainless steel wire
+with a diameter of \SI{0.5}{\milli\metre}. The reference resistor had multiple,
+parallel conductors, the ballast resistor had a bifilar winding, and both had
+air cores. These designs (see Figure \ref{fig:RefRes}) minimized electromagnetic
+interference and encouraged heat dissipation. Since the coaxial heater
+resistance measurement used a two-wire technique, the current-carrying circuit
+was made entirely of soldered joints to minimize stray resistance from
+developing in electrical connections.
+
+\begin{figure}
+\includegraphics[width=\textwidth]{RefRes.eps}%
+
+\caption{\label{fig:RefRes}An illustration of the designs of the ballast (left)
+and reference (right) resistors. The outside diameters of the coils are about
+\SI{25}{\milli\metre} and \SI{50}{\milli\metre} respectively. The designs
+emphasize heat dissipation by air convection and mitigation of electromagnetic
+interference by using parallel conductors.}
+
+\end{figure}
 
 The resistance of the reference resistor ($R_{ref}$) was about \SI{0.005}{\ohm},
-and the resistance of the coaxial heater ($R_{col}$) was about  \SI{0.3}{\ohm}, so
-that most of the heat in the circuit was dissipated by the coaxial heater.
-The potential difference across the coaxial heater ($V_{col}$) and the reference
-resistor ($V_{ref}$) were measured (See Figure \ref{Circuit}). If the
+the resistance of the coaxial heater ($R_{col}$) was about  \SI{0.3}{\ohm}, and
+the resistance of the ballast resistor was about \SI{0.01}{\ohm}, so that most
+of the heat in the circuit was dissipated by the coaxial heater.
+The potential differences across the coaxial heater ($V_{col}$) and the
+reference resistor ($V_{ref}$) were measured (See Figure \ref{fig:Circuit}). If the
 resistances of the coaxial heater and the reference resistor were both constant,
@@
 the temperature of the reference resistor does not change, then the ratio
-$V_{col}/V_{ref}$ will be proportional to $R_{col}$. If the resistance $R_{col}$ is
-assumed to be a monotonically rising function of the temperature ($R_{col} = f(T)$),
-then the inverse function will provide the temperature ($T = f^{-1}(R_{col})$).
+$V_{col}/V_{ref}$ will be proportional to $R_{col}$. If the resistance $R_{col}$
+is assumed to be a monotonically rising function of the temperature ($R_{col} =
+f(T)$), then the inverse function will provide the temperature ($T =
+f^{-1}(R_{col})$). In practice the voltage $V_{ref}$ is too small to be
+digitized directly and needs to be amplified to $V_b$, but it can be shown that
+$R_{col}$ is a function of $\left(\frac{dV}{V_b}\right)$, where $dV$ is the
+difference between the supply voltage and $V_b$. $dV$ and $V_b$ are of
+magnitudes that can be conveniently digitized.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{./Figures/ResistanceMeasurement.pdf}%
-\caption{\label{Circuit}A simplified circuit diagram of the resistance measuring circuit.}%
+\includegraphics[width=\textwidth]{Column-Heater.pdf}%
+\caption{\label{fig:Circuit}A simplified circuit diagram of the resistance measuring circuit.}%
 \end{figure}
@@
 A bank of six PNP 2N2955 bipolar transistors mounted in parallel on an aluminium
-plate provided a controlled current of up to \SI{20}{\ampere} at \SI{20}{\volt}
-for the coaxial heater. Their mounting plate was air-cooled by two 4-inch fans.
-
-A two-stage control system controlled the current. The first stage of the
-control system was a PID controller implemented in LabVIEW. The process variable
-was the temperature of the coaxial heater, as calculated from its electrical
-resistance, and the set value was determined by the desired chromatographic
-temperature program. The manipulated variable was the voltage of the
-digital-to-analog converter converter (DAC) of the data acquisition board. The
-final stage was an electronic system, where the voltage applied to the coaxial
-heater was the process variable, and the set value was a voltage provided by the
-DAC. The manipulated variable was the base current of the power transistors.
-In summary, the software set a voltage, which set the power of the coaxial
-heater. The two-stage design allows for switching of the control of the coaxial
-heater from computer control to manual control by a potentiometer on the
-instrument front panel. Being able to control the power of the coaxial heater
-manually is extremely useful during development and fault-finding.
+plate air-cooled by two 4-inch fans controlled a current of up to
+\SI{20}{\ampere} at \SI{20}{\volt} through the coaxial heater. A two-stage
+control system controlled the current. The first stage of the control system was
+a PID controller implemented in LabVIEW 7.1\texttrademark{} (National
+Instruments). The process variable was the temperature of the coaxial heater, as
+calculated from its electrical resistance, and the set value was determined by
+the desired chromatographic temperature program. The manipulated variable was
+the voltage of the digital-to-analog converter converter (DAC) of the data
+acquisition board. The final stage was an electronic system, where the voltage
+applied to the coaxial heater was the process variable, and the set value was a
+voltage provided by the DAC. The manipulated variable was the base current of
+the power transistors. In summary, the software set a voltage, which set the
+power of the coaxial heater. This two-stage design allows for switching of the
+control of the coaxial heater from computer control to manual control by a
+potentiometer on the instrument front panel. Being able to control the power of
+the coaxial heater manually is extremely useful during development and
+fault-finding.
 
 AD595 monolithic thermocouple amplifiers (Analog Devices) with integral cold
-junction compensation was used to condition the signal of the K-type
-thermocouples that were used for temperature monitoring and calibration.
-
-Solid state relays (Opto 22, Model 240D3) were used to switch the inlet and
-outlet T-piece block cartridge heaters (described above) on and off. Pulse width
+junction compensation were used to condition the signal of the K-type
+thermocouples that were used for temperature monitoring and calibration. Solid
+state relays (Opto 22, Model 240D3) were used to switch the inlet and outlet
+T-piece block cartridge heaters (described above) on and off. Pulse width
 modulation, implemented in software, was used to control the amount of heat
-produced by the cartridge heaters, and hence the temperature of the T-piece blocks.
-
-A PCI-6014 multifunction data acquisition board (National
+produced by the cartridge heaters, and hence the temperature of the T-piece
+blocks. A PCI-6014 multifunction data acquisition board (National
 Instruments\texttrademark{}) was used to interface the electronics with the
@@
 The temperature of the coaxial heater was calibrated by constructing a
-thermocouple probe from 0.025 mm diameter thermocouple alloy wire (T1 and T2
-alloys, Goodfellow) threaded inside a 500 mm length of 0.25 mm i.d.
-capillary chromatography column. This thermocouple was then threaded inside the
-coaxial heater (just like the capillary column during GC operation), to record
-the temperature of the heater. The recorded temperature could then be used to
-calibrate the coaxial heater resistance.
+thermocouple probe from \SI{0.025}{\milli\metre} diameter thermocouple alloy
+wire (T1 and T2 alloys, Goodfellow) threaded inside a \SI{1000}{\milli\metre}
+length of \SI{0.25}{\milli\metre} i.d. fused silica capillary. This thermocouple
+probe was then threaded inside the coaxial heater (just like the capillary
+column during GC operation) to record the temperature of the heater. The
+recorded temperature could then be used to calibrate the coaxial heater
+resistance.
 
@@
 To determine whether the coaxial heater was heating the column with acceptable
-uniformity, we used two methods. First, we acquired thermal images of the
-coaxial heater, using a FLIR T660 infrared camera. Secondly, for experiments in
-determining temperature gradients, a thermocouple probe was constructed as
-described above, except that the probe contained two thermocouples, 330 mm
-apart, equidistant from the ends.
+uniformity, we used two methods. Firstly, we acquired thermographic videos of
+the coaxial heater, using a FLIR T660 infrared camera. Secondly, for experiments
+in determining temperature gradients, a thermocouple probe was constructed as
+described above, except that the probe contained two thermocouples,
+\SI{330}{\milli\metre} apart, equidistant from the ends.
 
@@
 The software for controlling the instrument and collecting data was written in
-LabVIEW 7.1\texttrademark{} (National Instruments).
+LabVIEW. Two main loops were used. One controlled the various aspects of the
+instrument, in particular the temperature control, and ran with a period of
+\SI{200}{\milli\second}. The second main loop collected the data and ran as
+often as the hardware allowed.
+
 % The multi-threading capabilities of LabVIEW greatly eased development. Each
@@
 % loops simplified development.
-Two main loops were used. One controlled the various aspects of the instrument,
-in particular the temperature control. This loop ran with a  period of 200 ms.
-The second main loop collected the data and ran as often as the hardware
-allowed.
 
@@
 proportional-integral-derivative (PID) controllers implemented in LabVIEW. In
-practice it was found that only proportional and integrative control was needed.
+practice it was found that only proportional and integral control was needed.
 We used a privately published\cite{Peacock2008} step-by-step implementation of
-the Cohen-Coon loop tuning method.
-
-Subsidiary PID controllers controlled the T-piece block temperatures and the
-CO$_2$ pump pressure.
+the Cohen-Coon loop tuning method. Subsidiary PID controllers controlled the
+T-piece block temperatures and the CO$_2$ pump pressure.
 
@@
 \subsubsection{Data structure}
-In GC×GC, 2D data is recorded as a continuous FID output stream, as if it
-is a 1D GC chromatogram, and later converted into a 2D chromatogram, using
-knowledge of the modulation period.
-
-For two reasons we could not use this approach. Firstly, in our instrument the
-first (SFC) dimension runs in a stop-flow mode making continuous data recording
-inappropriate. Secondly, the duration of the cooling cycle can vary slightly,
-which could introduce unacceptable variation in \textsuperscript{2}D retention
-times.
-
-We therefore constructed 2D chromatograms by starting to record data each time
-the GC fast temperature program started, noting the GC start time as the elution
-time of the first (SFC) dimension.
+In GC×GC, 2D data is recorded as a continuous detector output stream, as if it
+were a 1D GC chromatogram, and later converted into a 2D chromatogram, using
+knowledge of the modulation period. For two reasons we could not use this
+approach. Firstly, in our instrument the first (SFC) dimension runs in a
+stop-flow mode making continuous data recording inappropriate. Secondly, the
+duration of the cooling cycle can vary slightly, which could introduce
+unacceptable variation in \textsuperscript{2}D retention times. We therefore
+started detector output recording at the start of each GC fast temperature
+program, using the GC start time as the elution time of the first (SFC)
+dimension.
 
@@
 For data visualization we used the technical computing system Mathematica
-11.3\texttrademark{} (Wolfram).  First the collected data was converted to a
+11.3\texttrademark{} (Wolfram).  The collected data was first converted to a
 list of three-element lists, with $^1$D retention time, $^2$D retention time,
 and detector signal as the elements of the inner lists. The Mathematica
-functions \texttt{List3DPlot[]} and \texttt{ContourPlot[]} could then be used to
+functions \texttt{List3DPlot[]} and \texttt{ContourPlot[]} was then used to
 plot 3D chromatograms or contour plots respectively.
@@
 question about its temperature uniformity. Because the temperature coefficient
-of resistivity of metals is positive, in the absence of equalizing heat flow the
-resistive heating process in a long, thin tube is inherently unstable. To
-monitor the temperature profile along the length, we acquired a thermal video
-(Figure \ref{fig:ThermImg}) of the coaxial heater. The video shows that the
-coaxial heater heats and cools smoothly with no run-away hot spots.
+of resistivity of metals is positive, in the absence of equalizing heat flow
+along the length of conductor the resistive heating process in a long, thin tube
+is inherently unstable. To monitor the temperature profile along its length we
+acquired a thermographic video of the coaxial heater (See Supplementary Online
+Material). The video shows that the coaxial heater heats and cools smoothly with
+no run-away hot spots. A still image from the video is show in Figure
+\ref{fig:ThermImg}.
 
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{./Figures/1-16.jpg}%
-\caption{\label{fig:ThermImg}A thermal image of the coaxial heater.}%
+  \includegraphics[width=\textwidth]{1-16.pdf}%
+  \caption{\label{fig:ThermImg} A frame from the thermographic video of the coaxial heater. There are no evident run-away hot spots.}%
 \end{figure}
@@
 was inserted into the coaxial heater. The two thermocouples in the probe were
-330 mm apart and positioned in the central third of the coaxial heater. The
-coaxial heater was submitted to a repeated program of cooling and ballistic
-heating. Figure \ref{fig:Repeatability} shows that the gradients established by
-cooling was small (approximately \SI{10}{\celsius}), stable and repeatable, and
-should not prevent good chromatography.
+\SI{330}{\milli\metre} apart and positioned in the central third of the coaxial
+heater. The coaxial heater was submitted to a repeated program of cooling and
+ballistic heating. The recorded data (see Figure \ref{fig:Repeatability}) shows
+that the two thermocouples reported different temperatures and that the
+difference changed during the heating, implying that the coaxial heater did not
+cool or heat perfectly uniformly. But the temperature differences between the
+two points were small (approximately \SI{10}{\celsius} at most), stable, and
+repeatable and should not prevent good chromatography. These data also show that
+ballistic heating is not repeatable enough for gas chromatography, as can be
+seen in the variation in temperatures at the end of the heating runs.
 
 \begin{figure}
-	\includegraphics[width=\textwidth]{./Figures/cp.pdf}%
-	\caption{\label{fig:Repeatability}A graph indicating that temperature gradients are modest, stable and repeatable}%
+  \includegraphics[width=\textwidth]{cp.pdf}%
+
+  \caption{\label{fig:Repeatability} The temperature difference between two
+  points in the coaxial heater. The temperature difference established during
+  cooling is reversed during heating, which shows that gradients exist, but they
+  are small and repeatable.}
+
 \end{figure}
@@
 calibration, because a single point (the junction of the thermocouple) needs to
-be in equilibrium with the length of the coaxial heater during the whole of fast
+be in equilibrium with the length of the coaxial heater during the full fast
 heating cycle. This equilibrium would be very difficult to maintain, especially
 because the uniformity of heating cannot be guaranteed, and is additionally
-influenced by the presence of the T-piece heaters at the high temperature of the
-GC inlet and detector --- for a totally uniform heating of the coaxial heater
-the T-piece blocks would have to be at the same temperature as the coaxial
-heater. Acknowledging these limitations, we performed a calibration procedure
-assuming that the thermocouple junction was in equilibrium with the coaxial
-heater, which was assumed to be of uniform temperature over its length.
-
-% In a more pragmatic approach we did some experiments to determine how much of a
-%temperature difference can be generated in the coaxial heater. A
-%dual-thermocouple probe was constructed, and used to measure temperatures 330 mm
-%apart in the coaxial heater. Using this we could determine that the temperature
-%gradients along the length of the coaxial heater generated by heating and
-%cooling was modest, stable and repeatable.
-
-%This convinced us that a resistance measurement calibrated against temperature
-%would furnish a meaningful measure of real temperature, as long as one kept the
-%non-linearity in mind.
-
-For reasons not understood, the calibration (see Figure \ref{TempCal}) curve is
-oddly curved, and we arbitrarily fitted a B-spline to the data points. This
-procedure can be automated\cite{WenniZheng2012}. Points from this B-spline curve
-were then extracted to create a calibration curve, from which an estimate of the
-temperature can be calculated by linear interpolation\cite{Possolo2017}.
+influenced by the presence of the hot T-piece blocks --- for a totally uniform
+heating of the coaxial heater the T-piece blocks would have to be at the same
+temperature as the coaxial heater. Acknowledging these limitations, we performed
+a calibration procedure assuming that the thermocouple junction was in
+equilibrium with the coaxial heater, which was assumed to be of uniform
+temperature over its length. Because these assumptions are simplifications, or
+for other overlooked reasons, the calibration curve (see Figure
+\ref{fig:TempCal}) is oddly curved, and we arbitrarily fitted a B-spline to the
+data points. This procedure can be automated\cite{Zheng2012}. Points from this
+B-spline curve were then extracted to create a calibration curve, from which an
+estimate of the temperature can be calculated by linear
+interpolation\cite{Possolo2017}.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{./Figures/2019_07_12_B-spline_fit_CPlot.pdf}%
-
-\caption{\label{TempCal}A calibration curve of the coaxial heater. The markers
-were obtained from a B-spline fitted manually to the curve. The temperature is
-obtained by linear interpolation between markers.}%
+\includegraphics[width=\textwidth]{2019_07_12_B-spline_fit_CPlot.pdf}%
+
+\caption{\label{fig:TempCal}A calibration curve of the coaxial heater. The blue
+points represent the experimental data, and the red line is a B-spline fitted
+manually to the data. The red markers are points extracted from the B-spline.
+The temperature is obtained by linear interpolation between markers.}%
 
@@
 time\cite{Blumberg2000}. With hydrogen as carrier gas in a
-\SI{0.25}{\milli\metre} i.d. column of the optimum linear velocity is
+\SI{0.25}{\milli\metre} i.d. column the efficiency-optimized linear velocity is
 \SI{40}{\centi\metre\per\second}. Then the void time of a \SI{1}{\metre} column
-is \SI{2.5}{\s}, so the recommended heating rate is \SI{10}{\celsius} per
-\SI{2.5}{\s}, which is \SI{4}{\celsius}/s, or \SI{240}{\celsius\per\minute}.
-Since in fast chromatography excess peak resolution is traded for shorter run
-times, higher than optimum flow rates will be used, so higher heating rates will
-be required. For narrower columns the flow will be even higher so heating rates
-of more than \SI{1000}{\celsius\per\minute} will be required.
+is \SI{2.5}{\second}, so the recommended heating rate is \SI{10}{\celsius} per
+\SI{2.5}{\s}, which is \SI{4}{\celsius\per\second}, or
+\SI{240}{\celsius\per\minute}. Since in fast chromatography excess peak
+resolution is traded for shorter run times, higher-than-optimum flow rates will
+be used, so higher heating rates will be required. For narrower columns the flow
+will be even higher so that heating rates of more than
+\SI{1000}{\celsius\per\minute} will be required.
 
 The attainable heating rate is a function of power to the heater and of the
-temperature required. (In the instrument presented here power was limited by the
-voltage output range of the DAC of the data acquisition board, and not by the
-power of the heater.) We were able to maintain controlled heating rates of
+temperature required. (In the instrument presented here the power was limited by
+the voltage output range of the DAC of the data acquisition board, and not by
+the power of the heater.) We were able to maintain controlled heating rates of
 \SI{2500}{\celsius\per\minute} up to \SI{400}{\celsius}, or up to \SI{4000}{\celsius\per\minute}
-up to \SI{350}{\celsius}. (Figure \ref{fig:MaxHeatingRate}.) The heating rates
-attainable seem to be high enough for the most demanding fast gas
+up to \SI{350}{\celsius} (See Figure \ref{fig:MaxHeatingRate}). The heating
+rates attainable seem to be high enough for the most demanding fast gas
 chromatography.
@@
 \begin{figure}
-\includegraphics[width=\textwidth]{./Figures/high_rate_heating.pdf}%
-
-\caption{\label{fig:MaxHeatingRate}A graph of 9 identical, consecutive
+\includegraphics[width=\textwidth]{high_rate_heating.pdf}%
+
+\caption{\label{fig:MaxHeatingRate}A graph of \num{9} identical, consecutive
 temperature ramps overlaid. The heating rate is \SI{4000}{\celsius\per\minute}.
@@
 
-Comprehensively coupled chromatography depends heavily on repeatable
+Comprehensive two-dimensional chromatography depends heavily on repeatable
 \textsuperscript{2}D separations. To test for chromatographic repeatability, we
 added small amounts of hydrocarbons to the \textsuperscript{1}D mobile phase.
-They are unretained on the silica stationary phase. Because they are not
-retained, they are present in every fraction of the SFC eluate in equal amounts,
-and therefore they should yield identical \textsuperscript{2}D chromatograms.
-
-Results obtained from creating a 2D blank chromatogram with two alkanes in the
-mobile phase is summarized in Table \ref{tab:table1}. The peak widths were about
-\SI{500}{\milli\second}, so the \SI{20}{\milli\second} standard deviation for
-hexadecane means that the variation in retention time is only about
-\SI{10}{\percent} of the peak width. The relative standard deviations (RSD) of
-retention times were similar to those obtained in GC×GC\cite{Shellie2002}.
+They are unretained on the silica stationary phase and are therefore present in
+every fraction of the SFC eluate in equal amounts and should yield identical
+\textsuperscript{2}D chromatograms. Results obtained from creating a 2D blank
+chromatogram with two alkanes in the mobile phase are summarized in Table
+\ref{tab:table1}. The peak widths were about \SI{500}{\milli\second}, so the
+\SI{20}{\milli\second} standard deviation for hexadecane means that the
+variation in retention time is only about \SI{10}{\percent} of the peak width.
+The relative standard deviations (RSD) of retention times were similar to those
+obtained in GC×GC\cite{Shellie2002}.
 
@@
 
-Comprehensively coupled chromatography is made possible by having different
+Comprehensive two-dimensional chromatography is made possible by having different
 retention mechanisms in the columns of the two dimensions. When fatty acid
-methyl esters (FAMEs) are chromatographically separated on bare silica with pure
+methyl esters (FAMEs) are chromatographically separated on bare silica with neat
 carbon dioxide as a mobile phase, they are separated according to the number of
@@
 into the pure carbon dioxide mobile phase at \SI{200}{\bar} and room temperature
-and eluted through bare silica.
-
-We collected 10-second fractions of SFC eluate on the cold GC column. The fast
-temperature program ramped the GC column temperature from \SI{-20}{\celsius} to
-\SI{350}{\celsius} in \SI{10}{s} (\SI{2200}{\celsius\per\second}), then
-maintaining \SI{350}{\celsius} for \SI{2}{\second}. Then the cooling system
-would activate and cool the column to \SI{-20}{\celsius} or below, ready to trap
-the next SFC fraction.
-
-In this way a series of GC chromatograms of SFC fractions were recorded, which
-could be assembled into a 2D chromatogram. Figure \ref{fig:2DChromatogram} shows
-a 2D chromatogram of a sample of FAME prepared from canola oil. This 2D
-chromatogram consists of 132 fast GC chromatograms collected in approximately 90
-minutes.
+and eluted through bare silica. We collected \SI{10}{\second} fractions of SFC
+eluate on the cold GC column. The fast temperature program ramped the GC column
+temperature from \SI{-20}{\celsius} to \SI{350}{\celsius} in \SI{10}{s}
+(\SI{2200}{\celsius\per\second}), then maintaining \SI{350}{\celsius} for
+\SI{2}{\second}. Then the cooling system would activate and cool the column to
+\SI{-20}{\celsius} or below, ready to trap the next SFC fraction. In this way a
+series of GC chromatograms of SFC fractions were recorded to build up a 2D
+chromatogram. Figure \ref{fig:2DChromatogram} shows a 2D chromatogram of a
+sample of FAME prepared from canola oil. This 2D chromatogram consists of
+\num{132} fast GC chromatograms collected in approximately \SI{90}{\minute}.
 
 \begin{figure}
-\includegraphics[width=\textwidth]{./Figures/Interpretation.png}%
+  \includegraphics[width=\textwidth]{Interpretation.eps}
 
@@
 canola oil. It is clear that the oil consists mostly of unsaturated fatty
-acids.}%
+acids.}
 
@@
 In the supplementary material we provide a thermographic video of the coaxial
-heater heating and cooling, which indicates the evenness of heating and the
-rapidity of cooling.
+heater heating and cooling, which demonstrates the even of heating of the
+coaxial heater and its rapid cooling by evaporating carbon dioxide.
 
@@
 the generous donation of the packed silica columns. Reinhardt Heymans from FLIR
-Systems recorded the thermal images at no cost. David Masemula kept the
+Systems recorded the thermographic videos at no cost. David Masemula kept the
 laboratory supplied with consumables.
@@
 % Create the reference section using BibTeX:
-\bibliography{RSI-2019_05}
+%\bibliography{RSI-2019_05}
 % Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"
+%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{34}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Watson}, \citenamefont {Horton},\ and\ \citenamefont
+  {Staples}(1991)}]{Watson1991}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Watson}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Horton}}, \
+  and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Staples}},\ }in\
+  \href {\doibase 10.1109/ULTSYM.1991.234175} {\emph {\bibinfo {booktitle}
+  {IEEE 1991 Ultrasonics Symposium,}}},\ Vol.~\bibinfo {volume} {1}\ (\bibinfo
+  {year} {1991})\ pp.\ \bibinfo {pages} {305--309}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {He}, \citenamefont {Liu},\ and\ \citenamefont
+  {Liu}(2014)}]{He2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {He}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Liu}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ }in\ \href
+  {\doibase 10.1109/SPAWDA.2014.6998526} {\emph {\bibinfo {booktitle}
+  {Proceedings of the 2014 Symposium on Piezoelectricity, Acoustic Waves, and
+  Device Applications}}}\ (\bibinfo {year} {2014})\ pp.\ \bibinfo {pages}
+  {59--64}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hupp}\ \emph {et~al.}(2018)\citenamefont {Hupp},
+  \citenamefont {Perron}, \citenamefont {Roques}, \citenamefont {Crandall},
+  \citenamefont {Ramos},\ and\ \citenamefont {Rohrback}}]{Hupp2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont
+  {Hupp}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Perron}},
+  \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont {Roques}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Crandall}}, \bibinfo {author}
+  {\bibfnamefont {S.}~\bibnamefont {Ramos}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Rohrback}},\ }\href {\doibase
+  https://doi.org/10.1016/j.fuel.2018.05.102} {\bibfield  {journal} {\bibinfo
+  {journal} {Fuel}\ }\textbf {\bibinfo {volume} {231}},\ \bibinfo {pages} {264
+  } (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2014)\citenamefont {Chen},
+  \citenamefont {Zhang}, \citenamefont {Liu}, \citenamefont {Chen},
+  \citenamefont {Piao}, \citenamefont {Zhang}, \citenamefont {Wu},
+  \citenamefont {Zhong}, \citenamefont {Sun}, \citenamefont {Zou},
+  \citenamefont {Zhang}, \citenamefont {Wan}, \citenamefont {Wang},\ and\
+  \citenamefont {Yan}}]{Chen2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {X.}~\bibnamefont
+  {Chen}}, \bibinfo {author} {\bibfnamefont {X.~L.}\ \bibnamefont {Zhang}},
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Liu}}, \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont
+  {M.~Y.}\ \bibnamefont {Piao}}, \bibinfo {author} {\bibfnamefont {F.~J.}\
+  \bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont {W.~D.}\ \bibnamefont
+  {Wu}}, \bibinfo {author} {\bibfnamefont {Y.~B.}\ \bibnamefont {Zhong}},
+  \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Sun}}, \bibinfo {author}
+  {\bibfnamefont {Y.~C.}\ \bibnamefont {Zou}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Wan}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Wang}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Yan}},\
+  }\href {\doibase 10.1093/bja/aeu193} {\bibfield  {journal} {\bibinfo
+  {journal} {British Journal of Anaesthesia}\ }\textbf {\bibinfo {volume}
+  {113}},\ \bibinfo {pages} {807} (\bibinfo {year} {2014})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dong}\ \emph {et~al.}(2017)\citenamefont {Dong},
+  \citenamefont {Zhang}, \citenamefont {Wang}, \citenamefont {Wang},
+  \citenamefont {Guo}, \citenamefont {Kanhar}, \citenamefont {Chen},
+  \citenamefont {Liu}, \citenamefont {Zhou}, \citenamefont {Yan},\ and\
+  \citenamefont {Chen}}]{Dong2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Dong}}, \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Zhang}},
+  \bibinfo {author} {\bibfnamefont {F.~Y.}\ \bibnamefont {Wang}}, \bibinfo
+  {author} {\bibfnamefont {Y.~Y.}\ \bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Guo}}, \bibinfo {author} {\bibfnamefont
+  {G.~M.}\ \bibnamefont {Kanhar}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Liu}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Zhou}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Yan}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Chen}},\ }\href {\doibase
+  10.1016/j.chroma.2017.05.001} {\bibfield  {journal} {\bibinfo  {journal}
+  {Journal of Chromatography A}\ }\textbf {\bibinfo {volume} {1506}},\ \bibinfo
+  {pages} {93} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Górska-Horczyczak}\ \emph
+  {et~al.}(2017)\citenamefont {Górska-Horczyczak}, \citenamefont
+  {Wojtasik-Kalinowska}, \citenamefont {Guzek}, \citenamefont {Sun},\ and\
+  \citenamefont {Wierzbicka}}]{Gorska-Horczyczak2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Górska-Horczyczak}}, \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Wojtasik-Kalinowska}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Guzek}}, \bibinfo {author} {\bibfnamefont {D.-W.}\ \bibnamefont {Sun}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Wierzbicka}},\
+  }\href {\doibase 10.1111/jfpe.12540} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Food Process Engineering}\ }\textbf {\bibinfo {volume}
+  {40}},\ \bibinfo {pages} {e12540} (\bibinfo {year} {2017})},\ \Eprint
+  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1111/jfpe.12540}
+  {https://onlinelibrary.wiley.com/doi/pdf/10.1111/jfpe.12540} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {White}(2015)}]{White2015}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
+  {White}},\ }\href
+  {http://www.sciencedirect.com/science/article/pii/S0021967315010791}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\
+  }\textbf {\bibinfo {volume} {1421}},\ \bibinfo {pages} {129} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liu}\ and\ \citenamefont {Phillips}(1991)}]{Liu1991}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont
+  {Liu}}\ and\ \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont
+  {Phillips}},\ }\href {\doibase 10.1093/chromsci/29.6.227} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Chromatographic Science}\ }\textbf
+  {\bibinfo {volume} {29}},\ \bibinfo {pages} {227} (\bibinfo {year}
+  {1991})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Seeley}\ and\ \citenamefont
+  {Seeley}(2013)}]{Seeley2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~V.}\ \bibnamefont
+  {Seeley}}\ and\ \bibinfo {author} {\bibfnamefont {S.~K.}\ \bibnamefont
+  {Seeley}},\ }\href {\doibase 10.1021/ac303195u} {\bibfield  {journal}
+  {\bibinfo  {journal} {Anal. Chem.}\ }\textbf {\bibinfo {volume} {85}},\
+  \bibinfo {pages} {557} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Prebihalo}\ \emph {et~al.}(2018)\citenamefont
+  {Prebihalo}, \citenamefont {Berrier}, \citenamefont {Freye}, \citenamefont
+  {Bahaghighat}, \citenamefont {Moore}, \citenamefont {Pinkerton},\ and\
+  \citenamefont {Synovec}}]{Prebihalo2018}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.~E.}\ \bibnamefont
+  {Prebihalo}}, \bibinfo {author} {\bibfnamefont {K.~L.}\ \bibnamefont
+  {Berrier}}, \bibinfo {author} {\bibfnamefont {C.~E.}\ \bibnamefont {Freye}},
+  \bibinfo {author} {\bibfnamefont {H.~D.}\ \bibnamefont {Bahaghighat}},
+  \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont {Moore}}, \bibinfo
+  {author} {\bibfnamefont {D.~K.}\ \bibnamefont {Pinkerton}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Synovec}},\ }\href {\doibase
+  10.1021/acs.analchem.7b04226} {\bibfield  {journal} {\bibinfo  {journal}
+  {Analytical Chemistry}\ }\textbf {\bibinfo {volume} {90}},\ \bibinfo {pages}
+  {505} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cramers}\ \emph {et~al.}(1999)\citenamefont
+  {Cramers}, \citenamefont {Janssen}, \citenamefont {{Van Deursen}},\ and\
+  \citenamefont {Leclercq}}]{Cramers1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~A.}\ \bibnamefont
+  {Cramers}}, \bibinfo {author} {\bibfnamefont {H.~G.}\ \bibnamefont
+  {Janssen}}, \bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont {{Van
+  Deursen}}}, \ and\ \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont
+  {Leclercq}},\ }\href {\doibase 10.1016/S0021-9673(99)00227-7} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf
+  {\bibinfo {volume} {856}},\ \bibinfo {pages} {315} (\bibinfo {year}
+  {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Korytár}\ \emph {et~al.}(2002)\citenamefont
+  {Korytár}, \citenamefont {Janssen}, \citenamefont {Matisová},\ and\
+  \citenamefont {Brinkman}}]{Korytar2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Korytár}}, \bibinfo {author} {\bibfnamefont {H.-G.}\ \bibnamefont
+  {Janssen}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Matisová}},
+  \ and\ \bibinfo {author} {\bibfnamefont {U.~A.}\ \bibnamefont {Brinkman}},\
+  }\href {\doibase https://doi.org/10.1016/S0165-9936(02)00811-7} {\bibfield
+  {journal} {\bibinfo  {journal} {TrAC Trends in Analytical Chemistry}\
+  }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {558 } (\bibinfo {year}
+  {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Giddings}(1995)}]{Giddings1995}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+  {Giddings}},\ }\href {\doibase 10.1016/0021-9673(95)00249-m} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf
+  {\bibinfo {volume} {703}},\ \bibinfo {pages} {3} (\bibinfo {year}
+  {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Camenzuli}\ and\ \citenamefont
+  {Schoenmakers}(2014)}]{Camenzuli2014}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Camenzuli}}\ and\ \bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont
+  {Schoenmakers}},\ }\href {\doibase 10.1016/j.aca.2014.05.048} {\bibfield
+  {journal} {\bibinfo  {journal} {Analytica Chimica Acta}\ }\textbf {\bibinfo
+  {volume} {838}},\ \bibinfo {pages} {93} (\bibinfo {year} {2014})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {de~Koning}\ \emph {et~al.}(2004)\citenamefont
+  {de~Koning}, \citenamefont {Janssen}, \citenamefont {van Deursen},\ and\
+  \citenamefont {Brinkman}}]{Koning2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {de~Koning}}, \bibinfo {author} {\bibfnamefont {H.-G.}\ \bibnamefont
+  {Janssen}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {van
+  Deursen}}, \ and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont
+  {Brinkman}},\ }\href {\doibase 10.1002/jssc.200301676} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Separation Science}\ }\textbf {\bibinfo
+  {volume} {27}},\ \bibinfo {pages} {397} (\bibinfo {year} {2004})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Venter}\ and\ \citenamefont
+  {Rohwer}(2004)}]{Venter2004}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Venter}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+  {Rohwer}},\ }\href {\doibase 10.1021/ac035538c} {\bibfield  {journal}
+  {\bibinfo  {journal} {Analytical chemistry}\ }\textbf {\bibinfo {volume}
+  {76}},\ \bibinfo {pages} {3699} (\bibinfo {year} {2004})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Skoog}, \citenamefont {Holler},\ and\ \citenamefont
+  {Crouch}(2007)}]{Skoog2007}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
+  {Skoog}}, \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Holler}}, \
+  and\ \bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont {Crouch}},\
+  }\href {https://UnivofPretoria.on.worldcat.org/oclc/77224390} {\emph
+  {\bibinfo {title} {Principles of instrumental analysis}}},\ \bibinfo
+  {edition} {sixth edition.}\ ed.\ (\bibinfo  {publisher} {Thomson
+  Brooks/Cole},\ \bibinfo {address} {Belmont, CA},\ \bibinfo {year}
+  {2007})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dallüge}, \citenamefont {Beens},\ and\ \citenamefont
+  {Brinkman}(2003)}]{Dalluege2003}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Dallüge}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beens}}, \
+  and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}},\
+  }\href {\doibase 10.1016/s0021-9673(03)00242-5} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
+  {volume} {1000}},\ \bibinfo {pages} {69} (\bibinfo {year}
+  {2003})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Venter}, \citenamefont {Rohwer},\ and\ \citenamefont
+  {Laubscher}(1999)}]{Venter1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Venter}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Rohwer}},
+  \ and\ \bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont {Laubscher}},\
+  }\href {\doibase 10.1016/s0021-9673(99)00137-5} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
+  {volume} {847}},\ \bibinfo {pages} {309} (\bibinfo {year}
+  {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Blumberg}\ and\ \citenamefont
+  {Klee}(2000)}]{Blumberg2000}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.~M.}\ \bibnamefont
+  {Blumberg}}\ and\ \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
+  {Klee}},\ }\href {\doibase
+  10.1002/1520-667x(2000)12:9<508::aid-mcs5>3.0.co;2-y} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Microcolumn Separations}\ }\textbf {\bibinfo
+  {volume} {12}},\ \bibinfo {pages} {508} (\bibinfo {year} {2000})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Wang}, \citenamefont {Tolley},\ and\ \citenamefont
+  {Lee}(2012)}]{Wang2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {H.~D.}\ \bibnamefont {Tolley}}, \
+  and\ \bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont {Lee}},\ }\href
+  {\doibase 10.1016/j.chroma.2012.05.021} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo {volume}
+  {1261}},\ \bibinfo {pages} {46} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Jacobs}, \citenamefont {Hilder},\ and\ \citenamefont
+  {Shellie}(2013)}]{Jacobs2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
+  {Jacobs}}, \bibinfo {author} {\bibfnamefont {E.~F.}\ \bibnamefont {Hilder}},
+  \ and\ \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Shellie}},\
+  }\href {\doibase 10.1016/j.aca.2013.04.063} {\bibfield  {journal} {\bibinfo
+  {journal} {Analytica Chimica Acta}\ }\textbf {\bibinfo {volume} {803}},\
+  \bibinfo {pages} {2} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chow}\ and\ \citenamefont
+  {Górecki}(2017)}]{Chow2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.-Y.~J.}\
+  \bibnamefont {Chow}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Górecki}},\ }\href {\doibase 10.1021/acs.analchem.7b02134} {\bibfield
+  {journal} {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf {\bibinfo
+  {volume} {89}},\ \bibinfo {pages} {8207} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Venter}, \citenamefont {Makgwane},\ and\
+  \citenamefont {Rohwer}(2006)}]{Venter2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Venter}}, \bibinfo {author} {\bibfnamefont {P.~R.}\ \bibnamefont
+  {Makgwane}}, \ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+  {Rohwer}},\ }\href {\doibase 10.1021/ac051693a} {\bibfield  {journal}
+  {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf {\bibinfo {volume}
+  {78}},\ \bibinfo {pages} {2051} (\bibinfo {year} {2006})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Luong}\ \emph {et~al.}(2006)\citenamefont {Luong},
+  \citenamefont {Gras}, \citenamefont {Mustacich},\ and\ \citenamefont
+  {Cortes}}]{Luong2006}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Luong}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Gras}},
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Mustacich}}, \ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Cortes}},\ }\href
+  {\doibase 10.1093/chromsci/44.5.253} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Chromatographic Science}\ }\textbf {\bibinfo {volume}
+  {44}},\ \bibinfo {pages} {253} (\bibinfo {year} {2006})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {{Zip Scientific}}(2008)}]{ZipScientific2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {{Zip Scientific}}},\
+  }\href {http://www.zipsci.com/chaser-cool-down.htm} {\enquote {\bibinfo
+  {title} {Fast cooling performance},}\ } (\bibinfo {year} {2008})\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dallüge}\ \emph {et~al.}(1999)\citenamefont
+  {Dallüge}, \citenamefont {Ou-Aissa}, \citenamefont {Vreuls}, \citenamefont
+  {Brinkman},\ and\ \citenamefont {Veraart}}]{Dalluege1999}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Dallüge}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Ou-Aissa}},
+  \bibinfo {author} {\bibfnamefont {J.~J.}\ \bibnamefont {Vreuls}}, \bibinfo
+  {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Veraart}},\ }\href {\doibase
+  10.1002/(SICI)1521-4168(19990801)22:8<459::AID-JHRC459>3.0.CO;2-G} {\bibfield
+   {journal} {\bibinfo  {journal} {Journal of High Resolution Chromatography}\
+  }\textbf {\bibinfo {volume} {22}},\ \bibinfo {pages} {459} (\bibinfo {year}
+  {1999})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {{VICI AG International}}(2019)}]{VICIAGI2019}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {{VICI AG
+  International}}},\ }\href {https://vici.com/gc/FTP-200.php} {\enquote
+  {\bibinfo {title} {Multichannel fast temperature programmer},}\ } (\bibinfo
+  {year} {2019})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Peacock}(2008)}]{Peacock2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Peacock}},\ }\href {http://www.pidtuning.net} {\enquote {\bibinfo {title}
+  {{PID} tuning blueprint},}\ }\bibinfo {howpublished} {Internet} (\bibinfo
+  {year} {2008})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zheng}\ \emph {et~al.}(2012)\citenamefont {Zheng},
+  \citenamefont {Bo}, \citenamefont {Liu},\ and\ \citenamefont
+  {Wang}}]{Zheng2012}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Zheng}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Bo}}, \bibinfo
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Wang}},\ }\href {\doibase
+  10.1016/j.cagd.2012.03.004} {\bibfield  {journal} {\bibinfo  {journal}
+  {Computer Aided Geometric Design}\ }\textbf {\bibinfo {volume} {29}},\
+  \bibinfo {pages} {448} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Possolo}\ and\ \citenamefont
+  {Iyer}(2017)}]{Possolo2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Possolo}}\ and\ \bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont
+  {Iyer}},\ }\href {\doibase 10.1063/1.4974274} {\bibfield  {journal} {\bibinfo
+   {journal} {Review of Scientific Instruments}\ }\textbf {\bibinfo {volume}
+  {88}},\ \bibinfo {pages} {011301} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Shellie}, \citenamefont {Xie},\ and\ \citenamefont
+  {Marriott}(2002)}]{Shellie2002}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
+  {Shellie}}, \bibinfo {author} {\bibfnamefont {L.-L.}\ \bibnamefont {Xie}}, \
+  and\ \bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont {Marriott}},\
+  }\href {\doibase 10.1016/s0021-9673(02)00961-5} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
+  {volume} {968}},\ \bibinfo {pages} {161} (\bibinfo {year}
+  {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Smith}\ \emph {et~al.}(2001)\citenamefont {Smith},
+  \citenamefont {Hyytiänen}, \citenamefont {Felipe},\ and\ \citenamefont
+  {Morris}}]{Smith2001}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~M.}\ \bibnamefont
+  {Smith}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hyytiänen}},
+  \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Felipe}}, \ and\
+  \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont {Morris}},\ }\href
+  {\doibase
+  https://doi.org/10.1002/1615-9314(20010301)24:3%3C208::AID-JSSC208%3E3.0.CO;2-P}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Separation Science}\
+  }\textbf {\bibinfo {volume} {24}},\ \bibinfo {pages} {208} (\bibinfo {year}
+  {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {AOCS}(2017)}]{AOCS2017}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibnamefont {AOCS}},\ }\enquote
+  {\bibinfo {title} {{AOCS} official method {Ce} 2-66},}\ in\ \href@noop {}
+  {\emph {\bibinfo {booktitle} {Official Methods and Recommended Practices of
+  the AOCS}}}\ (\bibinfo  {publisher} {{A}merican {O}il {C}hemists'
+  {S}ociety},\ \bibinfo {year} {2017})\ \bibinfo {edition} {7th}\
+  ed.\BibitemShut {Stop}%
+\end{thebibliography}%
 

### 2020-02-03 Journal/Response2/ResponseLetter2.tex
As submitted after second review.

--- 2020-01-04 Journal/ResponseLetter.tex
@@
 
-Thank you for your email dated 7 November 2019 enclosing the reviewers’ comments. We
+Thank you for your email dated 30 January 2020 enclosing the reviewers’ comments. We
 have carefully reviewed the comments and have revised the manuscript accordingly. Our
@@
 \Reviewer{\#1}
-\begin{response}{Abstract, last line: the sentence fragment 'separating fatty information" needs revision.
-	}
- 	The sentence was revised and clarified.
+\begin{response}{will [give an] acceptable}
+ 	The sentence was corrected.
 \end{response}
 
-\begin{response}{p3, orthogonal and general elution problem. In trying to wrap
-my head around this argument, I can't help but think that despite their comment
-about GC×GC wrap-around, it does seem that this would be even more of a problem
-in their current setup or those using LC-GC. The authors miss the opportunity to
-justify the need for fast temperature programmed GC in their second dimension.
-Perhaps laying their arguments out in more detail here would be useful.
+\begin{response}{middle paragraph. The sentence construction is complicated with the nested parentheses.
 } 
-The problem with the vagueness of the argument was identified. The paragraphs
-were changed to clarify how the general elution problem applies to
-multidimensional chromatography, and to emphasize that SFC×GC demands
-temperature programming in the GC dimension.
+The parentheses were removed and a sentence providing more detail was added.
 \end{response}
 
-\begin{response}{p6 last line, sentence structure needs revision.
-	}  The sentence was revised and clarified.
+\begin{response}{Also the text describes a micro union brazed onto the block,
+but the figure shows a drilled and tapped hole.
+}  Although the relevant figure was intended to be conceptual in nature, we
+agree that a difference between the text and the figure can be confusing. The
+figure was changed to match the text.
 \end{response}
 
-\begin{response}{p7, description of the connection blocks. Refer the reader to see Figure 1 here. 
-	}  A reference to Figure 1 was added.
+\begin{response}{p11 digital to analog converter converter . converter is repeated. 
+	}  The repeated word was removed. 
 \end{response}
 
-\begin{response}{Also, singular-plural confusion in :"These blocks fulfilled three roles: It (1) sealed ... "
+\begin{response}{p15. Chromatographically, would it be better if the warmer side of the column was towards the detector or towards the inlet?
 	}  
-	The confusion was cleared up. 
-\end{response}
-
-\begin{response}{Figure 1. It is not clear from the drawing that the cryogenic
-coolant actually enters the heater tube. While the dimensions of the drawing are
-perhaps selected to be according to scale, the reader would benefit from a
-little artistic liberty here. (g) "electrical connection" is a little vague.
-	} The figure was changed to add a schematic diagram that illustrate the coolant
-	flow, and the caption was clarified.
-\end{response}
-
-\begin{response}{p9. Reference resistor and ballast resistor. What are the
-dimensions of the wires used to construct these resistors? What is the
-resistance of the ballast? 
-	} 
-	The requested details were added, as well as a figure that shows the construction of the relevant resistors.
-\end{response}
-
-\begin{response}{p13, A. Heating uniformity. Text says video is shown in
-Figure3. Figure 3 is a screen capture of the video shown in Supplemental
-Material. Correct accordingly.
-	}
-	We recognize the inaccuracy, and the text was corrected. 
-\end{response}
-
-\begin{response}{ p13. Gradients by cooling. Not sure how this statement
-accurately reflects the repeated heating cycles shown in Figure 4. Further
-information and a more detailed description of Figure 4 is required. Does the
-difference between the two calibration points along the length of the column (33
-and 66 cm) increase with temperature? 
-	}  
-	The discussion on the gradients measured by thermocouple was revised and expanded for greater clarity. 
-\end{response}
-
-\begin{response}{Figure 5. Explain in the heading the blue and red lines.
-	}  
-	The caption was revised with a better description that includes an explanation of the colours.
-\end{response}
-
-\begin{response}{Figure 2. Can be improved by showing more details of the
-circuit, rather than just three resistors in series.
-	}  The figure was replaced by a more detailed one, and the description in the text was adapted to match the figure.   
-\end{response}
-
-\begin{response}{A few references appear incomplete. e.g. 17 and 29.}  
-	The bibliography was reviewed and all the incomplete references were updated.
-\end{response}
-
-\Reviewer{\#2}
-
-\begin{response}{p1 Abstract, sentence change: We demonstrate the fast
-chromatograph by separating fatty acid methyl esters by carbon number, which
-would be useful in the food and biodiesel industries.
-	}  
-	The sentence was clarified. 
-\end{response}
-
-\begin{response}{p2: This concept is called comprehensively coupled
-chromatography. For example, in comprehensively coupled gas chromatography
-(GC×GC). Confirm correct nomenclature in as published by Marriot in LCGC 2012.
-	} We thank the reviewers for drawing attention to using correct nomenclature. We
-	revised the manuscript to ensure the recommended nomenclature was used throughout.
-\end{response}
-
-\begin{response}{p2 Sentence change: The use of narrow-bore columns and thin
-films reduce run times by improving mass transfer between the mobile and
-stationary phases, resulting in analytes spending more time in the mobile phase
-allowing shorter retention times.
-
-	} We agree that the sentence needed clarification, but disagree with the
-	explanation. Improved mass transfer does not allow analytes to spend more time
-	in the mobile phase, but it does reduce peak broadening.  The sentence was
-	revised thusly: \textit{Typically, short columns and high carrier flows rates
-	are used, which reduce retention times by reducing void times. Resolution can be
-	maintained at even higher gas flows by using narrow-bore columns and thin films:
-	these improve the mass transfer rate between the mobile and stationary phases,
-	which reduces peak broadening by bringing the analyte exchange between the
-	phases closer to equilibrium at higher-than-optimum carrier gas velocities.}
-
-\end{response}
-
-\begin{response}{p3 sentence change: it becomes unlikely that one set of
-acceptable operating conditions (temperature, flow and stationary phase) will
-give acceptable (fast enough and with adequate resolution) separation in both
-dimensions.
-	}  This sentence was revised as part of general improvement in the argument.
-	(See Reviewer 1, comment ``p.3'')
-\end{response}
-
-\begin{response}{p3 sentence change: so late that the next modulation period has
-already started before its elution and the peak only appears on the next 2D
-chromatogram 
-	}  The sentence was revised as suggested.
-\end{response}
-
-\begin{response}{p3 sentence change: If wraparound is a problem in GC×GC, it
-becomes inevitable in SFC×GC since the first dimension (SFC) does not normally
-separate compounds in a way that correlates with vapour pressure.
-	}  This sentence was improved by revising the paragraph. 
-\end{response}
-
-\begin{response}{p5 sentence change: The Zip ScienticTM solution operates by forced convection.}  
-	The sentence was changed to the suggested one. 
-\end{response}
-
-\begin{response}{p5: sentence change: In our case we applied it as a fast second
-dimension separation, comprehensively coupled to a supercritical fluid
-chromatograph.
-	}  The sentence was changed to the suggested one. 
-\end{response}
-
-\begin{response}{p6 clarification: clarify what type of static restriction was
-used.
-	}  The description of the static restrictor was improved. 
-\end{response}
-
-\begin{response}{p6: sentence change: the stop valve opens and the SFC eluate
-exits the restrictor into the hot splitless inlet of the GC, where it evaporates
-and is transported onto the GC column.
-	}  This sentence was improved by rewriting the paragraph. 
-\end{response}
-
-\begin{response}{p6: sentence change: which of course means the start of the
-temperature program, which desorbs the analyteS trapped on the head of the cold
-column.
-	}  This sentence was improved by rewriting the paragraph.
-\end{response}
-
-\begin{response}{p7: sentence change: The split vent valve was disconnected from
-the gas chromatograph CONTROL and CONNECTED TO the control computer described
-below 
-	}  The sentence was changed to the suggested one. 
-\end{response}
-
-\begin{response}{p10: Figure 2: Figure do not contain that much detail and may
-be omitted.
-	}  The figure was replace by a more detailed one, and the text adapted to match
-	the figure. (See Reviewer 1, comment ``Figure 2'')
-\end{response}
-
-\begin{response}{p12: abbreviation: LabVIEW 7.1TM (National Instruments). This
-abbreviation was used earlier p10 and should be clarified there.
-	}  We recognize the oversight and corrected it.
-\end{response}
-
-\begin{response}{p15: sentence change: In the instrument presented here, THE
-power was limited by the voltage output range of the DAC of the data acquisition
-board, and not by the power of the heater.
-	}  The sentence was replaced by the suggested one.
+	A sentence and a citation was added to show a possible benefit if the warmer end of the column was towards the inlet.
 \end{response}

### 2020-02-03 document.tex
As submitted after second review.

@@
 that one set of acceptable operating conditions (temperature, flow and
-stationary phase) will an give acceptable (fast enough and with adequate
+stationary phase) will an give an acceptable (fast enough and with adequate
 resolution) $^2$D separation. In GC×GC as it is practised today this has become
@@
 T-piece block via the bottom port with the coaxial heater tube and passed out
-through the top port (where a micro-union using a metal ferrule
+through the top port, where a micro-union using a metal ferrule
 (Restek\texttrademark{} SilTite $\mu$-Union Connectors) brazed to the block
-created a seal to contain the coolant) and into the inlet or detector.
+created a seal to contain the coolant. From the top port the the column crossed
+a small, electrically isolating air gap before entering the inlet or detector.
 
@@
 The reference and ballast resistors were constructed from stainless steel wire
-with a diameter of \SI{0.5}{\milli\metre}. The reference resistor had multiple,
+with a diameter of \SI{1.0}{\milli\metre}. The reference resistor had multiple,
 parallel conductors, the ballast resistor had a bifilar winding, and both had
@@
 the desired chromatographic temperature program. The manipulated variable was
-the voltage of the digital-to-analog converter converter (DAC) of the data
+the voltage of the digital-to-analog converter (DAC) of the data
 acquisition board. The final stage was an electronic system, where the voltage
@@
 two points were small (approximately \SI{10}{\celsius} at most), stable, and
-repeatable and should not prevent good chromatography. These data also show that
-ballistic heating is not repeatable enough for gas chromatography, as can be
-seen in the variation in temperatures at the end of the heating runs.
+repeatable and should not prevent good chromatography. In fact, a small
+longitudinal gradient, with the lower temperature nearer the detector, will
+produce sharper peaks\cite{Contreras2013}. These data also show that ballistic
+heating is not repeatable enough for gas chromatography, as can be seen in the
+variation in temperatures at the end of the heating runs.
 
@@
 % Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"
-%merlin.mbs aipnum4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% BBL file contents start
+%aipnum4-2.bst 2019-01-14 (MD) hand-edited version of apsrev4-1.bst
 %Control: key (0)
@@
 %Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
+%Control: production of article title (0) allowed
+%Control: page (1) range
 %Control: year (1) truncated
 %Control: production of eprint (0) enabled
-\begin{thebibliography}{34}%
+\begin{thebibliography}{35}%
 \makeatletter
@@
 \providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \doibase [0]{https://doi.org/}%
 \providecommand \selectlanguage [0]{\@gobble}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Watson}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Horton}}, \
-  and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Staples}},\ }in\
-  \href {\doibase 10.1109/ULTSYM.1991.234175} {\emph {\bibinfo {booktitle}
-  {IEEE 1991 Ultrasonics Symposium,}}},\ Vol.~\bibinfo {volume} {1}\ (\bibinfo
-  {year} {1991})\ pp.\ \bibinfo {pages} {305--309}\BibitemShut {NoStop}%
+  {Watson}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Horton}},\
+  and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Staples}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Gas chromatography utilizing
+  saw sensors},}\ }in\ \href {https://doi.org/10.1109/ULTSYM.1991.234175}
+  {\emph {\bibinfo {booktitle} {IEEE 1991 Ultrasonics Symposium,}}},\
+  Vol.~\bibinfo {volume} {1}\ (\bibinfo {year} {1991})\ pp.\ \bibinfo {pages}
+  {305--309}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {He}, \citenamefont {Liu},\ and\ \citenamefont
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {He}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Liu}}, \ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ }in\ \href
-  {\doibase 10.1109/SPAWDA.2014.6998526} {\emph {\bibinfo {booktitle}
-  {Proceedings of the 2014 Symposium on Piezoelectricity, Acoustic Waves, and
-  Device Applications}}}\ (\bibinfo {year} {2014})\ pp.\ \bibinfo {pages}
-  {59--64}\BibitemShut {NoStop}%
+  {He}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Liu}},\ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Research progress of saw gas
+  charomatography},}\ }in\ \href {https://doi.org/10.1109/SPAWDA.2014.6998526}
+  {\emph {\bibinfo {booktitle} {Proceedings of the 2014 Symposium on
+  Piezoelectricity, Acoustic Waves, and Device Applications}}}\ (\bibinfo
+  {year} {2014})\ pp.\ \bibinfo {pages} {59--64}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Hupp}\ \emph {et~al.}(2018)\citenamefont {Hupp},
@@
   {author} {\bibfnamefont {J.}~\bibnamefont {Crandall}}, \bibinfo {author}
-  {\bibfnamefont {S.}~\bibnamefont {Ramos}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Rohrback}},\ }\href {\doibase
-  https://doi.org/10.1016/j.fuel.2018.05.102} {\bibfield  {journal} {\bibinfo
-  {journal} {Fuel}\ }\textbf {\bibinfo {volume} {231}},\ \bibinfo {pages} {264
-  } (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+  {\bibfnamefont {S.}~\bibnamefont {Ramos}},\ and\ \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Rohrback}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Analysis of biodiesel-diesel blends using ultrafast gas
+  chromatography (ufgc) and chemometric methods: Extending astm d7798 to
+  biodiesel},}\ }\href
+  {https://doi.org/https://doi.org/10.1016/j.fuel.2018.05.102} {\bibfield
+  {journal} {\bibinfo  {journal} {Fuel}\ }\textbf {\bibinfo {volume} {231}},\
+  \bibinfo {pages} {264 -- 270} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2014)\citenamefont {Chen},
@@
   {D.}~\bibnamefont {Wan}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Wang}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Yan}},\
-  }\href {\doibase 10.1093/bja/aeu193} {\bibfield  {journal} {\bibinfo
-  {journal} {British Journal of Anaesthesia}\ }\textbf {\bibinfo {volume}
-  {113}},\ \bibinfo {pages} {807} (\bibinfo {year} {2014})}\BibitemShut
-  {NoStop}%
+  {Wang}},\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Yan}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {{Gas chromatograph-surface
+  acoustic wave for quick real-time assessment of blood/exhaled gas ratio of
+  propofol in humans}},}\ }\href {https://doi.org/10.1093/bja/aeu193}
+  {\bibfield  {journal} {\bibinfo  {journal} {British Journal of Anaesthesia}\
+  }\textbf {\bibinfo {volume} {113}},\ \bibinfo {pages} {807--814} (\bibinfo
+  {year} {2014})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Dong}\ \emph {et~al.}(2017)\citenamefont {Dong},
@@
   {Liu}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Zhou}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Yan}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {X.}~\bibnamefont {Chen}},\ }\href {\doibase
-  10.1016/j.chroma.2017.05.001} {\bibfield  {journal} {\bibinfo  {journal}
-  {Journal of Chromatography A}\ }\textbf {\bibinfo {volume} {1506}},\ \bibinfo
-  {pages} {93} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+  {author} {\bibfnamefont {M.}~\bibnamefont {Yan}},\ and\ \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Chen}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Simultaneous on-line monitoring of propofol and
+  sevoflurane in balanced anesthesia by direct resistive heating gas
+  chromatography}},}\ }\href {https://doi.org/10.1016/j.chroma.2017.05.001}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\
+  }\textbf {\bibinfo {volume} {1506}},\ \bibinfo {pages} {93--100} (\bibinfo
+  {year} {2017})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Górska-Horczyczak}\ \emph
@@
   {Wojtasik-Kalinowska}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Guzek}}, \bibinfo {author} {\bibfnamefont {D.-W.}\ \bibnamefont {Sun}}, \
+  {Guzek}}, \bibinfo {author} {\bibfnamefont {D.-W.}\ \bibnamefont {Sun}},\
   and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Wierzbicka}},\
-  }\href {\doibase 10.1111/jfpe.12540} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Food Process Engineering}\ }\textbf {\bibinfo {volume}
-  {40}},\ \bibinfo {pages} {e12540} (\bibinfo {year} {2017})},\ \Eprint
-  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1111/jfpe.12540}
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Differentiation of
+  chill-stored and frozen pork necks using electronic nose with ultra-fast gas
+  chromatography},}\ }\href {https://doi.org/10.1111/jfpe.12540} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Food Process Engineering}\
+  }\textbf {\bibinfo {volume} {40}},\ \bibinfo {pages} {e12540} (\bibinfo
+  {year} {2017})},\ \Eprint
+  {https://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1111/jfpe.12540}
   {https://onlinelibrary.wiley.com/doi/pdf/10.1111/jfpe.12540} \BibitemShut
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
-  {White}},\ }\href
+  {White}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Evolved gas
+  composition monitoring by repetitive injection gas chromatography},}\ }\href
   {http://www.sciencedirect.com/science/article/pii/S0021967315010791}
   {\bibfield  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\
-  }\textbf {\bibinfo {volume} {1421}},\ \bibinfo {pages} {129} (\bibinfo {year}
-  {2015})}\BibitemShut {NoStop}%
+  }\textbf {\bibinfo {volume} {1421}},\ \bibinfo {pages} {129--136} (\bibinfo
+  {year} {2015})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Liu}\ and\ \citenamefont {Phillips}(1991)}]{Liu1991}%
@@
   {Liu}}\ and\ \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont
-  {Phillips}},\ }\href {\doibase 10.1093/chromsci/29.6.227} {\bibfield
+  {Phillips}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Comprehensive
+  two-dimensional gas chromatography using an on-column thermal modulator
+  interface},}\ }\href {https://doi.org/10.1093/chromsci/29.6.227} {\bibfield
   {journal} {\bibinfo  {journal} {Journal of Chromatographic Science}\ }\textbf
-  {\bibinfo {volume} {29}},\ \bibinfo {pages} {227} (\bibinfo {year}
+  {\bibinfo {volume} {29}},\ \bibinfo {pages} {227--231} (\bibinfo {year}
   {1991})}\BibitemShut {NoStop}%
@@
   {Seeley}}\ and\ \bibinfo {author} {\bibfnamefont {S.~K.}\ \bibnamefont
-  {Seeley}},\ }\href {\doibase 10.1021/ac303195u} {\bibfield  {journal}
-  {\bibinfo  {journal} {Anal. Chem.}\ }\textbf {\bibinfo {volume} {85}},\
-  \bibinfo {pages} {557} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+  {Seeley}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Multidimensional
+  gas chromatography: Fundamental advances and new applications},}\ }\href
+  {https://doi.org/10.1021/ac303195u} {\bibfield  {journal} {\bibinfo
+  {journal} {Anal. Chem.}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo {pages}
+  {557--578} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Prebihalo}\ \emph {et~al.}(2018)\citenamefont
@@
   \bibinfo {author} {\bibfnamefont {N.~R.}\ \bibnamefont {Moore}}, \bibinfo
-  {author} {\bibfnamefont {D.~K.}\ \bibnamefont {Pinkerton}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Synovec}},\ }\href {\doibase
-  10.1021/acs.analchem.7b04226} {\bibfield  {journal} {\bibinfo  {journal}
-  {Analytical Chemistry}\ }\textbf {\bibinfo {volume} {90}},\ \bibinfo {pages}
-  {505} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+  {author} {\bibfnamefont {D.~K.}\ \bibnamefont {Pinkerton}},\ and\ \bibinfo
+  {author} {\bibfnamefont {R.~E.}\ \bibnamefont {Synovec}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Multidimensional gas chromatography:
+  Advances in instrumentation, chemometrics, and applications},}\ }\href
+  {https://doi.org/10.1021/acs.analchem.7b04226} {\bibfield  {journal}
+  {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf {\bibinfo {volume}
+  {90}},\ \bibinfo {pages} {505--532} (\bibinfo {year} {2018})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Cramers}\ \emph {et~al.}(1999)\citenamefont
@@
   {Janssen}}, \bibinfo {author} {\bibfnamefont {M.~M.}\ \bibnamefont {{Van
-  Deursen}}}, \ and\ \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont
-  {Leclercq}},\ }\href {\doibase 10.1016/S0021-9673(99)00227-7} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf
-  {\bibinfo {volume} {856}},\ \bibinfo {pages} {315} (\bibinfo {year}
+  Deursen}}},\ and\ \bibinfo {author} {\bibfnamefont {P.~A.}\ \bibnamefont
+  {Leclercq}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {High-speed gas
+  chromatography: An overview of various concepts},}\ }\href
+  {https://doi.org/10.1016/S0021-9673(99)00227-7} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
+  {volume} {856}},\ \bibinfo {pages} {315--329} (\bibinfo {year}
   {1999})}\BibitemShut {NoStop}%
@@
   {Korytár}}, \bibinfo {author} {\bibfnamefont {H.-G.}\ \bibnamefont
-  {Janssen}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Matisová}},
-  \ and\ \bibinfo {author} {\bibfnamefont {U.~A.}\ \bibnamefont {Brinkman}},\
-  }\href {\doibase https://doi.org/10.1016/S0165-9936(02)00811-7} {\bibfield
+  {Janssen}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Matisová}},\
+  and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Practical fast gas
+  chromatography: methods, instrumentation and applications},}\ }\href
+  {https://doi.org/https://doi.org/10.1016/S0165-9936(02)00811-7} {\bibfield
   {journal} {\bibinfo  {journal} {TrAC Trends in Analytical Chemistry}\
-  }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {558 } (\bibinfo {year}
-  {2002})}\BibitemShut {NoStop}%
+  }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {558 -- 572} (\bibinfo
+  {year} {2002})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Giddings}(1995)}]{Giddings1995}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
-  {Giddings}},\ }\href {\doibase 10.1016/0021-9673(95)00249-m} {\bibfield
-  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf
-  {\bibinfo {volume} {703}},\ \bibinfo {pages} {3} (\bibinfo {year}
+  {Giddings}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sample
+  dimensionality: A predictor of order-disorder in component peak distribution
+  in multidimensional separation},}\ }\href
+  {https://doi.org/10.1016/0021-9673(95)00249-m} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
+  {volume} {703}},\ \bibinfo {pages} {3--15} (\bibinfo {year}
   {1995})}\BibitemShut {NoStop}%
@@
   {Camenzuli}}\ and\ \bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont
-  {Schoenmakers}},\ }\href {\doibase 10.1016/j.aca.2014.05.048} {\bibfield
-  {journal} {\bibinfo  {journal} {Analytica Chimica Acta}\ }\textbf {\bibinfo
-  {volume} {838}},\ \bibinfo {pages} {93} (\bibinfo {year} {2014})}\BibitemShut
-  {NoStop}%
+  {Schoenmakers}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {A new
+  measure of orthogonality for multi-dimensional chromatography},}\ }\href
+  {https://doi.org/10.1016/j.aca.2014.05.048} {\bibfield  {journal} {\bibinfo
+  {journal} {Analytica Chimica Acta}\ }\textbf {\bibinfo {volume} {838}},\
+  \bibinfo {pages} {93--101} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {de~Koning}\ \emph {et~al.}(2004)\citenamefont
@@
   {Janssen}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {van
-  Deursen}}, \ and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont
-  {Brinkman}},\ }\href {\doibase 10.1002/jssc.200301676} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Separation Science}\ }\textbf {\bibinfo
-  {volume} {27}},\ \bibinfo {pages} {397} (\bibinfo {year} {2004})}\BibitemShut
-  {NoStop}%
+  Deursen}},\ and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont
+  {Brinkman}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Automated
+  on-line comprehensive two-dimensional {LC}{\texttimes}{GC} and
+  {LC}{\texttimes}{GC}-{ToF} {MS}: Instrument design and application to edible
+  oil and fat analysis},}\ }\href {https://doi.org/10.1002/jssc.200301676}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Separation Science}\
+  }\textbf {\bibinfo {volume} {27}},\ \bibinfo {pages} {397--409} (\bibinfo
+  {year} {2004})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Venter}\ and\ \citenamefont
@@
   {Venter}}\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
-  {Rohwer}},\ }\href {\doibase 10.1021/ac035538c} {\bibfield  {journal}
-  {\bibinfo  {journal} {Analytical chemistry}\ }\textbf {\bibinfo {volume}
-  {76}},\ \bibinfo {pages} {3699} (\bibinfo {year} {2004})}\BibitemShut
-  {NoStop}%
+  {Rohwer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Comprehensive
+  two-dimensional supercritical fluid and gas chromatography with independent
+  fast programmed heating of the gas chromatographic column.}}\ }\href
+  {https://doi.org/10.1021/ac035538c} {\bibfield  {journal} {\bibinfo
+  {journal} {Analytical chemistry}\ }\textbf {\bibinfo {volume} {76}},\
+  \bibinfo {pages} {3699--706} (\bibinfo {year} {2004})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Skoog}, \citenamefont {Holler},\ and\ \citenamefont
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~A.}\ \bibnamefont
-  {Skoog}}, \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Holler}}, \
+  {Skoog}}, \bibinfo {author} {\bibfnamefont {F.~J.}\ \bibnamefont {Holler}},\
   and\ \bibinfo {author} {\bibfnamefont {S.~R.}\ \bibnamefont {Crouch}},\
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Dallüge}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beens}}, \
+  {Dallüge}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Beens}},\
   and\ \bibinfo {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}},\
-  }\href {\doibase 10.1016/s0021-9673(03)00242-5} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
-  {volume} {1000}},\ \bibinfo {pages} {69} (\bibinfo {year}
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Comprehensive
+  two-dimensional gas chromatography: a powerful and versatile analytical
+  tool},}\ }\href {https://doi.org/10.1016/s0021-9673(03)00242-5} {\bibfield
+  {journal} {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf
+  {\bibinfo {volume} {1000}},\ \bibinfo {pages} {69--108} (\bibinfo {year}
   {2003})}\BibitemShut {NoStop}%
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Venter}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Rohwer}},
-  \ and\ \bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont {Laubscher}},\
-  }\href {\doibase 10.1016/s0021-9673(99)00137-5} {\bibfield  {journal}
+  {Venter}}, \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont {Rohwer}},\
+  and\ \bibinfo {author} {\bibfnamefont {A.~E.}\ \bibnamefont {Laubscher}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Analysis of alkane, alkene,
+  aromatic and oxygenated groups in petrochemical mixtures by supercritical
+  fluid chromatography on silica gel},}\ }\href
+  {https://doi.org/10.1016/s0021-9673(99)00137-5} {\bibfield  {journal}
   {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
-  {volume} {847}},\ \bibinfo {pages} {309} (\bibinfo {year}
+  {volume} {847}},\ \bibinfo {pages} {309--321} (\bibinfo {year}
   {1999})}\BibitemShut {NoStop}%
@@
   {Blumberg}}\ and\ \bibinfo {author} {\bibfnamefont {M.~S.}\ \bibnamefont
-  {Klee}},\ }\href {\doibase
-  10.1002/1520-667x(2000)12:9<508::aid-mcs5>3.0.co;2-y} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Microcolumn Separations}\ }\textbf {\bibinfo
-  {volume} {12}},\ \bibinfo {pages} {508} (\bibinfo {year} {2000})}\BibitemShut
-  {NoStop}%
+  {Klee}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Optimal heating
+  rate in gas chromatography},}\ }\href
+  {https://doi.org/10.1002/1520-667x(2000)12:9<508::aid-mcs5>3.0.co;2-y}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of Microcolumn
+  Separations}\ }\textbf {\bibinfo {volume} {12}},\ \bibinfo {pages} {508--514}
+  (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Wang}, \citenamefont {Tolley},\ and\ \citenamefont
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Wang}}, \bibinfo {author} {\bibfnamefont {H.~D.}\ \bibnamefont {Tolley}}, \
-  and\ \bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont {Lee}},\ }\href
-  {\doibase 10.1016/j.chroma.2012.05.021} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo {volume}
-  {1261}},\ \bibinfo {pages} {46} (\bibinfo {year} {2012})}\BibitemShut
-  {NoStop}%
+  {Wang}}, \bibinfo {author} {\bibfnamefont {H.~D.}\ \bibnamefont {Tolley}},\
+  and\ \bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont {Lee}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Gas chromatography using
+  resistive heating technology},}\ }\href
+  {https://doi.org/10.1016/j.chroma.2012.05.021} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
+  {volume} {1261}},\ \bibinfo {pages} {46--57} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Jacobs}, \citenamefont {Hilder},\ and\ \citenamefont
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~R.}\ \bibnamefont
-  {Jacobs}}, \bibinfo {author} {\bibfnamefont {E.~F.}\ \bibnamefont {Hilder}},
-  \ and\ \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Shellie}},\
-  }\href {\doibase 10.1016/j.aca.2013.04.063} {\bibfield  {journal} {\bibinfo
+  {Jacobs}}, \bibinfo {author} {\bibfnamefont {E.~F.}\ \bibnamefont {Hilder}},\
+  and\ \bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont {Shellie}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Applications of resistive
+  heating in gas chromatography: A review},}\ }\href
+  {https://doi.org/10.1016/j.aca.2013.04.063} {\bibfield  {journal} {\bibinfo
   {journal} {Analytica Chimica Acta}\ }\textbf {\bibinfo {volume} {803}},\
-  \bibinfo {pages} {2} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+  \bibinfo {pages} {2--14} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Chow}\ and\ \citenamefont
@@
   \bibnamefont {Chow}}\ and\ \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Górecki}},\ }\href {\doibase 10.1021/acs.analchem.7b02134} {\bibfield
-  {journal} {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf {\bibinfo
-  {volume} {89}},\ \bibinfo {pages} {8207} (\bibinfo {year}
+  {Górecki}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Temperature
+  programming of the second dimension in comprehensive two-dimensional gas
+  chromatography},}\ }\href {https://doi.org/10.1021/acs.analchem.7b02134}
+  {\bibfield  {journal} {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf
+  {\bibinfo {volume} {89}},\ \bibinfo {pages} {8207--8211} (\bibinfo {year}
   {2017})}\BibitemShut {NoStop}%
@@
   {Venter}}, \bibinfo {author} {\bibfnamefont {P.~R.}\ \bibnamefont
-  {Makgwane}}, \ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
-  {Rohwer}},\ }\href {\doibase 10.1021/ac051693a} {\bibfield  {journal}
-  {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf {\bibinfo {volume}
-  {78}},\ \bibinfo {pages} {2051} (\bibinfo {year} {2006})}\BibitemShut
-  {NoStop}%
+  {Makgwane}},\ and\ \bibinfo {author} {\bibfnamefont {E.~R.}\ \bibnamefont
+  {Rohwer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Group-type
+  analysis of oxygenated compounds with a silica gel porous layer open tubular
+  column and comprehensive two-dimensional supercritical fluid and gas
+  chromatography},}\ }\href {https://doi.org/10.1021/ac051693a} {\bibfield
+  {journal} {\bibinfo  {journal} {Analytical Chemistry}\ }\textbf {\bibinfo
+  {volume} {78}},\ \bibinfo {pages} {2051--2054} (\bibinfo {year}
+  {2006})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Luong}\ \emph {et~al.}(2006)\citenamefont {Luong},
@@
   {Luong}}, \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Gras}},
-  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Mustacich}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Cortes}},\ }\href
-  {\doibase 10.1093/chromsci/44.5.253} {\bibfield  {journal} {\bibinfo
+  \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont {Mustacich}},\ and\
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Cortes}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Low thermal mass gas chromatography:
+  Principles and applications},}\ }\href
+  {https://doi.org/10.1093/chromsci/44.5.253} {\bibfield  {journal} {\bibinfo
   {journal} {Journal of Chromatographic Science}\ }\textbf {\bibinfo {volume}
-  {44}},\ \bibinfo {pages} {253} (\bibinfo {year} {2006})}\BibitemShut
+  {44}},\ \bibinfo {pages} {253--261} (\bibinfo {year} {2006})}\BibitemShut
   {NoStop}%
@@
   \bibinfo {author} {\bibfnamefont {J.~J.}\ \bibnamefont {Vreuls}}, \bibinfo
-  {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Veraart}},\ }\href {\doibase
-  10.1002/(SICI)1521-4168(19990801)22:8<459::AID-JHRC459>3.0.CO;2-G} {\bibfield
-   {journal} {\bibinfo  {journal} {Journal of High Resolution Chromatography}\
-  }\textbf {\bibinfo {volume} {22}},\ \bibinfo {pages} {459} (\bibinfo {year}
-  {1999})}\BibitemShut {NoStop}%
+  {author} {\bibfnamefont {U.~A.~T.}\ \bibnamefont {Brinkman}},\ and\ \bibinfo
+  {author} {\bibfnamefont {J.~R.}\ \bibnamefont {Veraart}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Fast temperature programming in gas
+  chromatography using resistive heating},}\ }\href
+  {https://doi.org/10.1002/(SICI)1521-4168(19990801)22:8<459::AID-JHRC459>3.0.CO;2-G}
+  {\bibfield  {journal} {\bibinfo  {journal} {Journal of High Resolution
+  Chromatography}\ }\textbf {\bibinfo {volume} {22}},\ \bibinfo {pages}
+  {459--464} (\bibinfo {year} {1999})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {{VICI AG International}}(2019)}]{VICIAGI2019}%
@@
   {year} {2008})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Contreras}\ \emph {et~al.}(2013)\citenamefont
+  {Contreras}, \citenamefont {Rockwood}, \citenamefont {Tolley},\ and\
+  \citenamefont {Lee}}]{Contreras2013}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont
+  {Contreras}}, \bibinfo {author} {\bibfnamefont {A.~L.}\ \bibnamefont
+  {Rockwood}}, \bibinfo {author} {\bibfnamefont {H.~D.}\ \bibnamefont
+  {Tolley}},\ and\ \bibinfo {author} {\bibfnamefont {M.~L.}\ \bibnamefont
+  {Lee}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Peak sweeping and
+  gating using thermal gradient gas chromatography},}\ }\href
+  {https://doi.org/10.1016/j.chroma.2013.01.010} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
+  {volume} {1278}},\ \bibinfo {pages} {160--165} (\bibinfo {year}
+  {2013})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {Zheng}\ \emph {et~al.}(2012)\citenamefont {Zheng},
@@
   {Zheng}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Bo}}, \bibinfo
-  {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {W.}~\bibnamefont {Wang}},\ }\href {\doibase
-  10.1016/j.cagd.2012.03.004} {\bibfield  {journal} {\bibinfo  {journal}
-  {Computer Aided Geometric Design}\ }\textbf {\bibinfo {volume} {29}},\
-  \bibinfo {pages} {448} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+  {author} {\bibfnamefont {Y.}~\bibnamefont {Liu}},\ and\ \bibinfo {author}
+  {\bibfnamefont {W.}~\bibnamefont {Wang}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Fast b-spline curve fitting by l-{BFGS}},}\ }\href
+  {https://doi.org/10.1016/j.cagd.2012.03.004} {\bibfield  {journal} {\bibinfo
+  {journal} {Computer Aided Geometric Design}\ }\textbf {\bibinfo {volume}
+  {29}},\ \bibinfo {pages} {448--462} (\bibinfo {year} {2012})}\BibitemShut
+  {NoStop}%
 \bibitem [{\citenamefont {Possolo}\ and\ \citenamefont
@@
   {Possolo}}\ and\ \bibinfo {author} {\bibfnamefont {H.~K.}\ \bibnamefont
-  {Iyer}},\ }\href {\doibase 10.1063/1.4974274} {\bibfield  {journal} {\bibinfo
+  {Iyer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Invited article:
+  Concepts and tools for the evaluation of measurement uncertainty},}\ }\href
+  {https://doi.org/10.1063/1.4974274} {\bibfield  {journal} {\bibinfo
   {journal} {Review of Scientific Instruments}\ }\textbf {\bibinfo {volume}
@@
   \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~A.}\ \bibnamefont
-  {Shellie}}, \bibinfo {author} {\bibfnamefont {L.-L.}\ \bibnamefont {Xie}}, \
+  {Shellie}}, \bibinfo {author} {\bibfnamefont {L.-L.}\ \bibnamefont {Xie}},\
   and\ \bibinfo {author} {\bibfnamefont {P.~J.}\ \bibnamefont {Marriott}},\
-  }\href {\doibase 10.1016/s0021-9673(02)00961-5} {\bibfield  {journal}
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Retention time
+  reproducibility in comprehensive two-dimensional gas chromatography using
+  cryogenic modulation},}\ }\href
+  {https://doi.org/10.1016/s0021-9673(02)00961-5} {\bibfield  {journal}
   {\bibinfo  {journal} {Journal of Chromatography A}\ }\textbf {\bibinfo
-  {volume} {968}},\ \bibinfo {pages} {161} (\bibinfo {year}
+  {volume} {968}},\ \bibinfo {pages} {161--170} (\bibinfo {year}
   {2002})}\BibitemShut {NoStop}%
@@
   {Smith}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Hyytiänen}},
-  \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Felipe}}, \ and\
-  \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont {Morris}},\ }\href
-  {\doibase
-  https://doi.org/10.1002/1615-9314(20010301)24:3%3C208::AID-JSSC208%3E3.0.CO;2-P}
+  \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont {Felipe}},\ and\
+  \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont {Morris}},\ }\bibfield
+   {title} {\enquote {\bibinfo {title} {High resolution packed column
+  supercritical fluid chromatography of fatty acid methyl esters},}\ }\href
+  {https://doi.org/https://doi.org/10.1002/1615-9314(20010301)24:3%3C208::AID-JSSC208%3E3.0.CO;2-P}
   {\bibfield  {journal} {\bibinfo  {journal} {Journal of Separation Science}\
-  }\textbf {\bibinfo {volume} {24}},\ \bibinfo {pages} {208} (\bibinfo {year}
-  {2001})}\BibitemShut {NoStop}%
+  }\textbf {\bibinfo {volume} {24}},\ \bibinfo {pages} {208--212} (\bibinfo
+  {year} {2001})}\BibitemShut {NoStop}%
 \bibitem [{\citenamefont {AOCS}(2017)}]{AOCS2017}%
@@
 
+% BBL file contents end
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \end{document}

### 2020-02-03 document.tex
Edits text to link to integrated multimedia.

@@
 \SI{0.80}{\milli\metre}. The ends of the coaxial heater tube terminated in two
-identical, specially designed T-piece blocks, machined from brass (See Figure
+identical, specially designed T-piece blocks, machined from brass (see Figure
 \ref{fig:Manifold}). These blocks fulfilled three roles:
@@
 The potential differences across the coaxial heater ($V_{col}$) and the
-reference resistor ($V_{ref}$) were measured (See Figure \ref{fig:Circuit}). If the
+reference resistor ($V_{ref}$) were measured (see Figure \ref{fig:Circuit}). If the
 resistances of the coaxial heater and the reference resistor were both constant,
@@
 is inherently unstable. To monitor the temperature profile along its length we
-acquired a thermographic video of the coaxial heater (See Supplementary Online
-Material). The video shows that the coaxial heater heats and cools smoothly with
-no run-away hot spots. A still image from the video is show in Figure
-\ref{fig:ThermImg}.
+acquired a thermographic video of the coaxial heater. The video shows that the
+coaxial heater heats and cools smoothly with no run-away hot spots, as shown in
+Figure \ref{fig:ThermImg} (Multimedia view).
 
@@
 \begin{figure}
-  \includegraphics[width=\textwidth]{1-16.pdf}%
-  \caption{\label{fig:ThermImg} A frame from the thermographic video of the coaxial heater. There are no evident run-away hot spots.}%
+  \includegraphics[width=\textwidth]{FLIR0111.pdf}%
+
+  \caption{\label{fig:ThermImg} A frame from the thermographic video of the
+  coaxial heater. There are no evident run-away hot spots. (Multimedia view)}%
+
 \end{figure}
@@
 \SI{2500}{\celsius\per\minute} up to \SI{400}{\celsius}, or up to \SI{4000}{\celsius\per\minute}
-up to \SI{350}{\celsius} (See Figure \ref{fig:MaxHeatingRate}). The heating
+up to \SI{350}{\celsius} (see Figure \ref{fig:MaxHeatingRate}). The heating
 rates attainable seem to be high enough for the most demanding fast gas
@@
 % \end{table}
-
-\section*{Supplementary Material}
-
-In the supplementary material we provide a thermographic video of the coaxial
-heater heating and cooling, which demonstrates the even of heating of the
-coaxial heater and its rapid cooling by evaporating carbon dioxide.
 
@@
   }\bibfield  {title} {\enquote {\bibinfo {title} {Gas chromatography utilizing
-  saw sensors},}\ }in\ \href {https://doi.org/10.1109/ULTSYM.1991.234175}
+  {SAW} sensors},}\ }in\ \href {https://doi.org/10.1109/ULTSYM.1991.234175}
   {\emph {\bibinfo {booktitle} {IEEE 1991 Ultrasonics Symposium,}}},\
@@
   \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Liu}},\ }\bibfield
-  {title} {\enquote {\bibinfo {title} {Research progress of saw gas
-  charomatography},}\ }in\ \href {https://doi.org/10.1109/SPAWDA.2014.6998526}
+  {title} {\enquote {\bibinfo {title} {Research progress of {SAW} gas
+  chromatography},}\ }in\ \href {https://doi.org/10.1109/SPAWDA.2014.6998526}
   {\emph {\bibinfo {booktitle} {Proceedings of the 2014 Symposium on
@@
   {\bibinfo {title} {Analysis of biodiesel-diesel blends using ultrafast gas
-  chromatography (ufgc) and chemometric methods: Extending astm d7798 to
+  chromatography ({UFGC}) and chemometric methods: Extending {ASTM D7798} to
   biodiesel},}\ }\href
@@
   {\bibfnamefont {W.}~\bibnamefont {Wang}},\ }\bibfield  {title} {\enquote
-  {\bibinfo {title} {Fast b-spline curve fitting by l-{BFGS}},}\ }\href
+  {\bibinfo {title} {Fast {B-spline} curve fitting by l-{BFGS}},}\ }\href
   {https://doi.org/10.1016/j.cagd.2012.03.004} {\bibfield  {journal} {\bibinfo
